### 2021-10-11 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@80ae38a45188806bccccbee5330e86fe330788b2 🚀

%!TEX TS-program = xelatex
\documentclass[11pt]{article}

\usepackage[english]{babel}

\usepackage{amsmath,amssymb,amsfonts}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{stix2}
\usepackage[scaled]{helvet}
\usepackage[scaled]{inconsolata}

\usepackage{lastpage}

\usepackage{setspace}

\usepackage{ccicons}

\usepackage[hang,flushmargin]{footmisc}

\usepackage{geometry}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}

\usepackage{fancyhdr}
\renewcommand{\headrulewidth}{0pt}\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\makeatletter
\newcounter{tableno}
\newenvironment{tablenos:no-prefix-table-caption}{
  \caption@ifcompatibility{}{
    \let\oldthetable\thetable
    \let\oldtheHtable\theHtable
    \renewcommand{\thetable}{tableno:\thetableno}
    \renewcommand{\theHtable}{tableno:\thetableno}
    \stepcounter{tableno}
    \captionsetup{labelformat=empty}
  }
}{
  \caption@ifcompatibility{}{
    \captionsetup{labelformat=default}
    \let\thetable\oldthetable
    \let\theHtable\oldtheHtable
    \addtocounter{table}{-1}
  }
}
\makeatother

\usepackage{array}
\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
\let\PBS=\PreserveBackslash

\usepackage[breaklinks=true]{hyperref}
\hypersetup{colorlinks,%
citecolor=blue,%
filecolor=blue,%
linkcolor=blue,%
urlcolor=blue}
\usepackage{url}

\usepackage{caption}
\setcounter{secnumdepth}{0}
\usepackage{cleveref}

\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
\else\Gin@nat@width\fi}
\makeatother
\let\Oldincludegraphics\includegraphics
\renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=\maxwidth]{#1}}

\usepackage{longtable}
\usepackage{booktabs}

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}

\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc} % for \widthof, \maxof
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\maxof{\widthof{#1}}{\csllabelwidth}}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\geometry{verbose,letterpaper,tmargin=2.2cm,bmargin=2.2cm,lmargin=2.2cm,rmargin=2.2cm}

\usepackage{lineno}
\usepackage[nolists,noheads]{endfloat}

\pagestyle{plain}

\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000

\doublespacing

\fancypagestyle{normal}
{
  \fancyhf{}
  \fancyfoot[R]{\footnotesize\sffamily\thepage\ of \pageref*{LastPage}}
}
\begin{document}
\raggedright
\thispagestyle{empty}
{\Large\bfseries\sffamily Template to prepare preprints and manuscripts
using markdown and github actions}
\vskip 5em

%
\href{https://orcid.org/0000-0002-6506-6487}{Michael D.\,Catchen}%
%
\,\textsuperscript{1,2}

\textsuperscript{1}\,McGill University\quad \textsuperscript{2}\,Québec
Centre for Biodiversity Sciences

\textbf{Correspondance to:}\\
Michael D. Catchen --- \texttt{michael.catchen@mail.mcgill.ca}\\

\vfill
This work is released by its authors under a CC-BY 4.0 license\hfill\ccby\\
Last revision: \emph{\today}

\clearpage
\thispagestyle{empty}

\vfill

        {\bfseries Purpose:}\,This template provides a series of scripts
to render a markdown document into an interactive website and a series
of PDFs.\\%
        {\bfseries Motivation:}\,It makes collaborating on text with
GitHub easier, and means that we never need to think about the
output.\\%
        {\bfseries Internals:}\,GitHub actions and a series of python
scritpts. The markdown is handled with \texttt{pandoc}.\\%

\vfill

\clearpage
\linenumbers
\pagestyle{normal}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

This document is for brainstorming the Colorado bumblebee metaweb
prediction project.

\hypertarget{data}{%
\section{1 Data}\label{data}}

The data consists of two parts, the field data collected at three
stations across Colorado, and the GBIF metaweb data aggregated and
cleaned by Julian R. and a student.

\hypertarget{field-data}{%
\subsection{1.1 Field data}\label{field-data}}

This data consists of nearly-daily records of visits between bee and
flower species for the months August-October. Data is collected from
three field sites: 1) Rocky Mountain Biological Lab (RMBL) 2) Niwot
Ridge 3) Pikes Peak

each with tens of plots each across an elevational gradient, collected
for 7/4/3 summers total.

\emph{To be determined}: specific number of plots per site and years per
site

\hypertarget{gbif-metaweb}{%
\subsection{1.2 GBIF metaweb}\label{gbif-metaweb}}

This data of a network of bee/flower species which have a record of both
occurring on GBIF for locations at some spatial grain

\emph{To be determined}: how does the scale of spatial aggregation
affect properties of metaweb, how much taxonomic overlap is there with
field data?---We have a lot of field data on interactions, but we can't
validate predictions on taxa that aren't present in field data. As a
result validation can only be done on interactions for which both
species appear in field data.

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{a-predictive-model-to-make-spatially-explicit-network-prediction}{%
\subsection{A predictive model to make spatially explicit network
prediction}\label{a-predictive-model-to-make-spatially-explicit-network-prediction}}

The goal is two have two predictive models: interaction-predictor model
and a distribution-predictor model (a la Strydom \& Catchen et al.~2021,
figure 2).

The interaction-predictor model, \(f_i(s_i,s_j, \theta_i)\) predicts
interaction based on species-level features \((s_i, s_j)\), and is
trained on the field-data.

These features could include Phylogeny (to be determined: how available
are genomes or trees for these species) Environment/Climate Traits (to
be determined: what trait data is available, how annoying is it to
clean) Time (only for the phenology model, see 3.2 and 3.3)

The distribution-predictor model, \(f_s(s_i, \vec{x}, t)\) is trained on
GBIF data to predict the occurrence of species with features si at a
location in space x, and time t. Many options here. Here the species
level features could be Climatic variables derived from remote sensing
products. Co-occurence to make a JSDM Potentially weighted by phenology
information from field data. Time (only for the phenology model, see 3.2
and 3.3)

\hypertarget{combining-distribution-predictor-and-interaction-predictor-models}{%
\subsection{Combining distribution-predictor and interaction-predictor
models}\label{combining-distribution-predictor-and-interaction-predictor-models}}

Can split this into two based on how the distribution-predictor works.
If \(f_s\) predicts co-occurrence, then draw the species pool first and
predict interactions between the species in that pool. If \(f_s\) is a
single-species SDM, get the occurrence probability for each species p\_s
and compute the probability of observing interaction as function of the
product of occ. prob.

\hypertarget{results}{%
\section{Results}\label{results}}

After comparing different combinations of features/model structures and
finding the `best' performing model on validation data.

\hypertarget{figure-one-spatial-species-pool-and-network-prediction}{%
\subsection{Figure one: spatial species pool and network
prediction}\label{figure-one-spatial-species-pool-and-network-prediction}}

Figure that is two panels: a map of total species richness and a map of
network properties across Colorado. This model doesn't consider time,
only other predictors.

\hypertarget{figure-two-phenology}{%
\subsection{Figure two: Phenology}\label{figure-two-phenology}}

Same as figure one but consists of maps but at different times of the
year (e.g. March, June, August) and uses both an interaction-predictor
and distribution-predictor that incorporate time into predictions

\hypertarget{figure-three-climate}{%
\subsection{Figure three: Climate}\label{figure-three-climate}}

Much as climate change has shifted temperature gradients to get warmer
toward the poles, it has also moved temperature gradients up in
elevation.

We can get a CMIP6 forecast of temperature and precipitation, and then
predict how many observed interactions in the field data will no longer
have their composing species' distributions overlap. Decompose temporal
component of overlap from spatial component.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\hypertarget{references}{%
\section{References}\label{references}}

\end{document}

### 2021-10-11 preprint.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@80ae38a45188806bccccbee5330e86fe330788b2 🚀

--- 2021-10-11 draft.tex
@@
 %!TEX TS-program = xelatex
-\documentclass[11pt]{article}
+\documentclass[10pt,oneside]{article}
+\usepackage[fontsize=9pt]{scrextend}
 
@@
 \newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth}{#1}}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\geometry{verbose,letterpaper,tmargin=2.2cm,bmargin=2.2cm,lmargin=2.2cm,rmargin=2.2cm}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}\usepackage[table,dvipsnames]{xcolor}
 
-\usepackage{lineno}
-\usepackage[nolists,noheads]{endfloat}
+\geometry{includemp,
+            letterpaper,
+            top=2.4cm,
+            bottom=2.4cm,
+            left=1.0cm,
+            right=1.0cm,
+            marginparwidth=5cm,
+            marginparsep=1.0cm}
+
+\usepackage[singlelinecheck=off]{caption}
+
+\captionsetup{
+  font={small},
+  labelfont={bf},
+  format=plain,
+  labelsep=quad
+}
+
+\usepackage{floatrow}
+
+\floatsetup[figure]{margins=hangright,
+              facing=no,
+              capposition=beside,
+              capbesideposition={center,outside},
+              floatwidth=\textwidth}
+
+% \floatsetup[table]{margins=hangright,
+%              facing=no,
+%              capposition=beside,
+%              capbesideposition={center,outside},
+%              floatwidth=\textwidth}
 
@@
 
-\tolerance=1
-\emergencystretch=\maxdimen
-\hyphenpenalty=10000
-\hbadness=10000
+\setcounter{secnumdepth}{5}
 
-\doublespacing
+\usepackage{titlesec}
+
+\titleformat{\section}[block]
+{\normalfont\large\sffamily}
+{\thesection}{.5em}{\titlerule\\[.8ex]\bfseries}
+
+\titleformat{\subsection}[runin]
+{\normalfont\fontseries{b}\selectfont\filright\sffamily}
+{\thesubsection.}{.5em}{}
+
+\titleformat{\subsubsection}[runin]
+{\normalfont\itshape\rmfamily\bfseries}{\thesubsubsection}{1em}{}
+
+\fancypagestyle{firstpage}
+{
+   \fancyhf{}
+   \renewcommand{\headrulewidth}{0pt}
+   \fancyfoot[R]{\footnotesize\ccby}
+   \fancyfoot[L]{\footnotesize\sffamily\today}
+}
 
@@
 }
+
+\usepackage{tikz}
 \begin{document}
-\raggedright
-\thispagestyle{empty}
-{\Large\bfseries\sffamily Template to prepare preprints and manuscripts
-using markdown and github actions}
-\vskip 5em
+\pagestyle{normal}
+\thispagestyle{firstpage}
 
+\newcommand{\colorRule}[3][black]{\textcolor[HTML]{#1}{\rule{#2}{#3}}}
+
+\noindent {\LARGE \textbf{\textsf{Template to prepare preprints and
+manuscripts using markdown and github actions}}}
+
+\medskip
+\begin{flushleft}
+{\small
 %
@@
 \,\textsuperscript{1,2}
-
-\textsuperscript{1}\,McGill University\quad \textsuperscript{2}\,Québec
-Centre for Biodiversity Sciences
-
+\vskip 1em
+\textsuperscript{1}\,McGill University; \textsuperscript{2}\,Québec
+Centre for Biodiversity Sciences\\
+\vskip 1em
 \textbf{Correspondance to:}\\
 Michael D. Catchen --- \texttt{michael.catchen@mail.mcgill.ca}\\
+}
+\end{flushleft}
 
-\vfill
-This work is released by its authors under a CC-BY 4.0 license\hfill\ccby\\
-Last revision: \emph{\today}
+\vskip 2em
+\makebox[0pt][l]{\colorRule[CCCCCC]{2.0\textwidth}{0.5pt}}
+\vskip 2em
+\noindent
 
-\clearpage
-\thispagestyle{empty}
-
-\vfill
+\marginpar{\vskip 1em\flushright
+{\small{\bfseries Keywords}:\par
+pandoc\\pandoc-crossref\\github actions\\}
+}
 
@@
 
-\vfill
-
-\clearpage
-\linenumbers
-\pagestyle{normal}
+\vskip 2em
+\makebox[0pt][l]{\colorRule[CCCCCC]{2.0\textwidth}{0.5pt}}
+\vskip 2em
 

### 2021-10-12 src/01_clean_data.jl
some early code

@@ -1,0 +1,122 @@
+using DataFrames
+using DataFramesMeta
+using CSV
+using Shapefile
+
+# each row is a species and columns are range data, and list of counties 
+GBIF_bee_occurrence = CSV.read(joinpath("rawdata", "bmbl.bee.csv"), DataFrame)
+
+# each row is an interaction
+GBIF_bee_flower_interactions = CSV.read(joinpath("rawdata", "bumblebee_interactions.csv"), DataFrame)
+names(GBIF_bee_flower_interactions)
+
+
+
+ElkMeadowsInteractions = CSV.read(joinpath("rawdata", "ElkMeadowsBombus.csv"), DataFrame)
+names(ElkMeadowsInteractions)
+ElkMeadowsInteractions[!, "Ordinal day"]
+ElkMeadowsInteractions[!, "Plot"]
+ElkMeadowsInteractions[!, "Insect species name"]
+ElkMeadowsInteractions[!, "Plant species name"]
+
+
+RMBL_phenology = CSV.read(joinpath("rawdata", "caradonna_rmbl_flowering_phenology_data_EDI.csv"), DataFrame)
+names(RMBL_phenology)
+RMBL_phenology[!, "plant"]
+
+
+RMBL_interactions = CSV.read(joinpath("rawdata", "caradonna_rmbl_interaction_networks_data_EDI.csv"), DataFrame)
+names(RMBL_interactions)
+RMBL_interactions[!, "plant"]
+RMBL_interactions[!, "pollinator"]
+RMBL_interactions[!, "interactions"]
+RMBL_interactions[!, "site"]
+RMBL_interactions[!, "year"]
+RMBL_interactions[!, "day_of_year"]
+
+
+
+# okay 
+# pull gbif occurences for each sp.
+using SimpleSDMLayers, GBIF, Plots
+
+bounds = (left=-109.6, right=-102.4, top=40.995, bottom=37.01 )
+
+specieslist = ["Bombus appositus", "Bombus auricomus",
+"Bombus balteatus",
+"Bombus bifarius",
+"Bombus californicus",
+"Bombus centralis",
+"Bombus fernaldae",
+"Bombus fervidus",
+"Bombus flavifrons",
+"Bombus fraternus",
+"Bombus frigidus",
+"Bombus griseocollis",
+"Bombus huntii",
+"Bombus insularis",
+"Bombus melanopygus",
+"Bombus mixtus",
+"Bombus morrisoni",
+"Bombus nevadensis",
+"Bombus occidentalis",
[…]

### 2021-10-12 src/rawdata/bumblebeenetwork.R

@@ -1,0 +1,288 @@
+# Bumblebee network project
+# J. Resasco
+setwd("/Users/julianresasco 1/Documents/Data/Bumblebee networks")
+
+library(reshape2)
+library(bipartite)
+library(igraph)
+library(vegan)
+
+intr <- read.csv("bumblebee_interactions.csv")
+plnt <- read.csv("plants.csv")
+bmbe <- read.csv("bmbl.bee.csv")
+elkb <- read.csv("ElkMeadowsBombus.csv")
+
+head(intr)
+head(plnt)
+head(bmbe)
+head(elkb)
+
+# check data for slight variations of variable names
+sort(unique(intr$plant.ackerfield))
+sort(unique(intr$species.plant))
+sort(unique(intr$bumblebee))
+
+# remove species
+intr <- subset(intr, intr$plant.ackerfield != "UNKNOWN SP UNKNOWN SP")
+intr <- subset(intr, intr$plant.ackerfield != "NA NA")
+intr <- subset(intr, intr$species.plant != "sp.")
+dim(intr)
+occ = rep(1, dim(intr)[1])
+intr <- cbind(intr, occ)
+
+# a useful function to make quantitative matrices binary
+quant2bin<-function(matr)
+{
+    ij<-which(matr!=0,arr.ind=T)
+    matrb<-matrix(0,dim(matr)[1],dim(matr)[2])
+    matrb[ij]<-1
+    return(matrb)
+}
+
+# build Colorado metaweb
+# make long data into plant x pollinator matrix
+comw <- acast(intr, plant.ackerfield~bumblebee, 
+                value.var="occ", fun.aggregate = sum)
+
+# plotweb visualization  
+plotweb(comw, method="normal",arrow="both",bor.col.interaction="grey", y.width.low=0.02, y.width.high=0.02, col.high="tomato", col.low="yellow green", high.lablength=20, low.lablength=20, text.rot = 90)
+
+
+# build subweb from a focal time and/or site 
+
+# select focal county
+county = "Boulder"
+
+# select focal elevation for Elk Meadow
+elevat.min = 9500
+elevat.max = 10000
+
+# select focal season
+#season.min = 
+#season.max = 
+
+# subset plants to focal site and elevation
+plant.sub <- subset(plnt, plnt$Boulder == 1)
[…]

### 2021-10-12 src/01_clean_data.jl
bee maps

@@ -38,11 +38,12 @@ RMBL_interactions[!, "day_of_year"]
 
 # okay 
 # pull gbif occurences for each sp.
-using SimpleSDMLayers, GBIF, Plots
+using SimpleSDMLayers, GBIF, Plots, Measures
 
-bounds = (left=-109.6, right=-102.4, top=40.995, bottom=37.01 )
 
-specieslist = ["Bombus appositus", "Bombus auricomus",
+speciesstrs =
+["Bombus appositus", 
+"Bombus auricomus",
 "Bombus balteatus",
 "Bombus bifarius",
 "Bombus californicus",
@@ -66,57 +67,57 @@ specieslist = ["Bombus appositus", "Bombus auricomus",
 "Bombus sylvicola",
 "Bombus variabilis"]
 
-observations = occurrences(
-    GBIF.taxon(specieslist[3]; strict=true),
-    "hasCoordinate" => "true",
-    "country" => "US",
-    "decimalLatitude" => (bounds.bottom, bounds.top),
-    "decimalLongitude" => (bounds.left, bounds.right),
-    "limit" => 10000,
-)
+specieslist = GBIF.taxon.(speciesstrs)
 
-while length(observations) < size(observations)
-    occurrences!(observations)
+function getplot(s)
+    bounds = (left=-109.6, right=-102.4, top=40.995, bottom=37.01 )
+
+    observations = occurrences(
+        s, 
+        "hasCoordinate" => "true",
+        "country" => "US",
+        "decimalLatitude" => (bounds.bottom, bounds.top),
+        "decimalLongitude" => (bounds.left, bounds.right),
+        "limit" => 10000
+    )
+
+    size(observations) <= 0 && return
+
+    while length(observations) < size(observations)
+        occurrences!(observations)
+    end
+
+    elev = convert(Float32, SimpleSDMPredictor(WorldClim, Elevation;  bounds...))
+
+    path = joinpath("rawdata", "colorado_counties","Colorado_County_Boundaries.shp")
+    table = Shapefile.Table(path)
+    geoms = Shapefile.shapes(table)
+
+
+    plot(frame=:none, tickfont=4, xlim=(-109, -102), ylim=(37,41), size=(300,300))
+    plot!(elev, c=:Blues_9, colorbar=:none)
+    plot!(geoms, lc=:white, fa=0, lw=1)
+    scatter!(
+        longitudes(observations),
[…]

### 2021-10-13 src/01_clean_data.jl
ok

@@ -3,6 +3,9 @@ using DataFramesMeta
 using CSV
 using Shapefile
 
+
+using SimpleSDMLayers, GBIF, Plots
+
 # each row is a species and columns are range data, and list of counties 
 GBIF_bee_occurrence = CSV.read(joinpath("rawdata", "bmbl.bee.csv"), DataFrame)
 
@@ -11,8 +14,37 @@ GBIF_bee_flower_interactions = CSV.read(joinpath("rawdata", "bumblebee_interacti
 names(GBIF_bee_flower_interactions)
 
 
+"""
+    Get the names of plant species from GBIF metaweb and write them 
+    to 'plantnames.csv'.
+
+"""
+plant_full_species_names = convert(Vector{String},unique(GBIF_bee_flower_interactions[!, "plant.ackerfield"]))
+gbifplants = GBIF.taxon.(plant_full_species_names, strict=false)
+filter!(!isnothing, gbifplants)
+plantnames = DataFrame(species=[p.name for p in gbifplants])
+CSV.write(joinpath("cleandata", "plantnames.csv"), plantnames)
+
+
+
+"""
+    Get the names of bee species from GBIF metaweb and write them 
+    to 'beenames.csv'.
+
+"""
+bee_species_names = convert(Vector{String},unique(GBIF_bee_flower_interactions[!, "bumblebee"]))
+gbifbees = GBIF.taxon.(bee_species_names)
+filter!(!isnothing, gbifbees)
+beenames = DataFrame(species=[p.name for p in gbifbees])
+CSV.write(joinpath("cleandata", "beenames.csv"), beenames)
+
+
+
+
+
 
 ElkMeadowsInteractions = CSV.read(joinpath("rawdata", "ElkMeadowsBombus.csv"), DataFrame)
+
 names(ElkMeadowsInteractions)
 ElkMeadowsInteractions[!, "Ordinal day"]
 ElkMeadowsInteractions[!, "Plot"]
@@ -33,91 +65,3 @@ RMBL_interactions[!, "interactions"]
 RMBL_interactions[!, "site"]
 RMBL_interactions[!, "year"]
 RMBL_interactions[!, "day_of_year"]
-
-
-
-# okay 
-# pull gbif occurences for each sp.
-using SimpleSDMLayers, GBIF, Plots, Measures
-
-
-speciesstrs =
-["Bombus appositus", 
-"Bombus auricomus",
-"Bombus balteatus",
-"Bombus bifarius",
-"Bombus californicus",
[…]

### 2021-10-13 src/02_plant_sdms.jl

@@ -1,0 +1,58 @@
+bounds = (left=-109.6, right=-102.4, top=40.995, bottom=37.01 )
+
+observations = []
+
+
+
+function getplantplot(observations, nm)
+    elev = convert(Float32, SimpleSDMPredictor(WorldClim, Elevation;  bounds...))
+
+    path = joinpath("rawdata", "colorado_counties","Colorado_County_Boundaries.shp")
+    table = Shapefile.Table(path)
+    geoms = Shapefile.shapes(table)
+
+
+    plot(frame=:none, tickfont=4, xlim=(-109, -102), ylim=(37,41), size=(300,300))
+    plot!(elev, c=:Blues_9, colorbar=:none)
+    plot!(geoms, lc=:white, fa=0, lw=1)
+    scatter!(
+        longitudes(observations),
+        latitudes(observations);
+        lab="",
+        c=:white,
+        msc=:orange,
+        ms=3,
+        alpha=0.5,
+    )
+    title!(nm)
+end
+
+
+
+for pl in gbifplants
+    try
+        occ= occurrences(
+            pl, 
+            "hasCoordinate" => "true",
+            "country" => "US",
+            "decimalLatitude" => (bounds.bottom, bounds.top),
+            "decimalLongitude" => (bounds.left, bounds.right),
+            "limit" => 300
+        )
+
+        push!(observations, occ)
+    catch e
+        @info "failed on $pl with $e"
+    end
+end
+
+plantplts = []
+
+for (i,obs) in enumerate(observations)
+    push!(plantplts, getplantplot(obs, gbifplants[i].name))
+end
+
+
+plot(plantplts..., size=(5100,5100))
+
+savefig("elplanto.png")

### 2021-10-13 src/03_bee_sdms.jl

@@ -1,0 +1,82 @@
+
+
+
+speciesstrs =
+["Bombus appositus", 
+"Bombus auricomus",
+"Bombus balteatus",
+"Bombus bifarius",
+"Bombus californicus",
+"Bombus centralis",
+"Bombus fernaldae",
+"Bombus fervidus",
+"Bombus flavifrons",
+"Bombus fraternus",
+"Bombus frigidus",
+"Bombus griseocollis",
+"Bombus huntii",
+"Bombus insularis",
+"Bombus melanopygus",
+"Bombus mixtus",
+"Bombus morrisoni",
+"Bombus nevadensis",
+"Bombus occidentalis",
+"Bombus pensylvanicus",
+"Bombus rufocinctus",
+"Bombus suckleyi",
+"Bombus sylvicola",
+"Bombus variabilis"]
+
+specieslist = GBIF.taxon.(speciesstrs)
+
+function getplot(s)
+
+    observations = occurrences(
+        s, 
+        "hasCoordinate" => "true",
+        "country" => "US",
+        "decimalLatitude" => (bounds.bottom, bounds.top),
+        "decimalLongitude" => (bounds.left, bounds.right),
+        "limit" => 10000
+    )
+
+    size(observations) <= 0 && return
+
+    while length(observations) < size(observations)
+        occurrences!(observations)
+    end
+
+    elev = convert(Float32, SimpleSDMPredictor(WorldClim, Elevation;  bounds...))
+
+    path = joinpath("rawdata", "colorado_counties","Colorado_County_Boundaries.shp")
+    table = Shapefile.Table(path)
+    geoms = Shapefile.shapes(table)
+
+
+    plot(frame=:none, tickfont=4, xlim=(-109, -102), ylim=(37,41), size=(300,300))
+    plot!(elev, c=:Blues_9, colorbar=:none)
+    plot!(geoms, lc=:white, fa=0, lw=1)
+    scatter!(
+        longitudes(observations),
+        latitudes(observations);
+        lab="",
+        c=:white,
+        msc=:orange,
+        ms=3,
+        alpha=0.5,
+    )
+    title!(s.name)
+end
+
+
+
+plts = []
+
+for s in specieslist
+    push!(plts, getplot(s))
+end
+
+
+plot(plts..., size=(2000,2000))
+
+savefig("occurrence_and_elevation.png")

### 2021-10-13 src/04_genbank_query.jl

@@ -1,0 +1,20 @@
+using CSV, DataFrames
+
+
+bees = CSV.read(joinpath("cleandata", "beenames.csv"), DataFrame) # bees?
+
+targetfile = "genbank_bee_query.txt"
+
+# format is 
+# "Bombus appositus"[Organism] OR "Bombus auricomus"[Organism] OR ... etc.
+
+
+query = "$(bees.species[begin])[Organism] OR "
+
+for s in bees.species[2:end-1]
+    query = string(query, "$s [Organism] OR ")
+end
+
+query = string(query, "$(bees.species[end])[Organism]")
+
+

### 2021-10-13 src/04_genbank_query.jl
some cleaned plant seqs

@@ -3,18 +3,20 @@ using CSV, DataFrames
 
 bees = CSV.read(joinpath("cleandata", "beenames.csv"), DataFrame) # bees?
 
-targetfile = "genbank_bee_query.txt"
-
+plants = CSV.read(joinpath("cleandata", "plantnames.csv"), DataFrame)
 # format is 
 # "Bombus appositus"[Organism] OR "Bombus auricomus"[Organism] OR ... etc.
 
+function makequery(species)
+    query = "$(species[begin])[Organism] OR "
 
-query = "$(bees.species[begin])[Organism] OR "
+    for s in species[2:end-1]
+        query = string(query, "$s [Organism] OR ")
+    end
 
-for s in bees.species[2:end-1]
-    query = string(query, "$s [Organism] OR ")
+    query = string(query, "$(species[end])[Organism]")
 end
 
-query = string(query, "$(bees.species[end])[Organism]")
 
 
+makequery(plants.species)

### 2021-10-13 src/05_bee_tree.jl

@@ -1,0 +1,9 @@
+using Phylo
+using Plots
+
+ts = open(parsenewick, "cleandata/bee_consensus.tree")
+
+
+plot(ts)
+
+savefig("eltree.png")

### 2021-10-13 src/trees.R

@@ -1,0 +1,12 @@
+library(ape)
+library(ips)
+library(phytools)
+
+setwd("/home/michael/papers/ms_bumblebees/src")
+
+
+tr = read.tree("cleandata/bee_consensus.tree")
+
+plot(tr)
+nodelabels(tr)
+

### 2021-10-14 src/trees.R
nearly there with plant genes

@@ -4,9 +4,17 @@ library(phytools)
 
 setwd("/home/michael/papers/ms_bumblebees/src")
 
-
-tr = read.tree("cleandata/bee_consensus.tree")
+read.tree("cleandata/CONSENSUS.nex")
+tr = read.tree("cleandata/ee_consensus.tree")
 
 plot(tr)
-nodelabels(tr)
+nodelabels(tr$edge.length)
 
+
+
+setwd("/home/michael/papers/ms_bumblebees/src")
+
+tr = ips::read("inprog_plants.nex")
+
+plot(tr)
+nodelabels(tr$edge.length)

### 2021-10-14 src/01_clean_data.jl
reorg

@@ -1,67 +1,0 @@
-using DataFrames
-using DataFramesMeta
-using CSV
-using Shapefile
-
-
-using SimpleSDMLayers, GBIF, Plots
-
-# each row is a species and columns are range data, and list of counties 
-GBIF_bee_occurrence = CSV.read(joinpath("rawdata", "bmbl.bee.csv"), DataFrame)
-
-# each row is an interaction
-GBIF_bee_flower_interactions = CSV.read(joinpath("rawdata", "bumblebee_interactions.csv"), DataFrame)
-names(GBIF_bee_flower_interactions)
-
-
-"""
-    Get the names of plant species from GBIF metaweb and write them 
-    to 'plantnames.csv'.
-
-"""
-plant_full_species_names = convert(Vector{String},unique(GBIF_bee_flower_interactions[!, "plant.ackerfield"]))
-gbifplants = GBIF.taxon.(plant_full_species_names, strict=false)
-filter!(!isnothing, gbifplants)
-plantnames = DataFrame(species=[p.name for p in gbifplants])
-CSV.write(joinpath("cleandata", "plantnames.csv"), plantnames)
-
-
-
-"""
-    Get the names of bee species from GBIF metaweb and write them 
-    to 'beenames.csv'.
-
-"""
-bee_species_names = convert(Vector{String},unique(GBIF_bee_flower_interactions[!, "bumblebee"]))
-gbifbees = GBIF.taxon.(bee_species_names)
-filter!(!isnothing, gbifbees)
-beenames = DataFrame(species=[p.name for p in gbifbees])
-CSV.write(joinpath("cleandata", "beenames.csv"), beenames)
-
-
-
-
-
-
-ElkMeadowsInteractions = CSV.read(joinpath("rawdata", "ElkMeadowsBombus.csv"), DataFrame)
-
-names(ElkMeadowsInteractions)
-ElkMeadowsInteractions[!, "Ordinal day"]
-ElkMeadowsInteractions[!, "Plot"]
-ElkMeadowsInteractions[!, "Insect species name"]
-ElkMeadowsInteractions[!, "Plant species name"]
-
-
-RMBL_phenology = CSV.read(joinpath("rawdata", "caradonna_rmbl_flowering_phenology_data_EDI.csv"), DataFrame)
-names(RMBL_phenology)
-RMBL_phenology[!, "plant"]
-
-
[…]

### 2021-10-14 src/scripts/01_clean_data.jl

@@ -1,0 +1,78 @@
+using DataFrames
+using DataFramesMeta
+using CSV
+using Shapefile
+
+
+using SimpleSDMLayers, GBIF, Plots
+
+# each row is a species and columns are range data, and list of counties 
+GBIF_bee_occurrence = CSV.read(joinpath("rawdata", "bmbl.bee.csv"), DataFrame)
+
+# each row is an interaction
+GBIF_bee_flower_interactions = CSV.read(joinpath("rawdata", "bumblebee_interactions.csv"), DataFrame)
+names(GBIF_bee_flower_interactions)
+
+df_to_write = DataFrame(bee=[], plant=[])
+
+for row in 1:nrow(GBIF_bee_flower_interactions)
+   thisrow = GBIF_bee_flower_interactions[row, :]
+   bee, plant = thisrow["bumblebee"], thisrow["genus.plant"]
+
+   push!(df_to_write.bee, bee)
+   push!(df_to_write.plant, plant)
+end
+
+CSV.write( "tmpmetaweb.csv",df_to_write,)
+
+"""
+    Get the names of plant species from GBIF metaweb and write them 
+    to 'plantnames.csv'.
+
+"""
+plant_full_species_names = convert(Vector{String},unique(GBIF_bee_flower_interactions[!, "plant.ackerfield"]))
+gbifplants = GBIF.taxon.(plant_full_species_names, strict=false)
+filter!(!isnothing, gbifplants)
+plantnames = DataFrame(species=[p.name for p in gbifplants])
+CSV.write(joinpath("cleandata", "plantnames.csv"), plantnames)
+
+
+
+"""
+    Get the names of bee species from GBIF metaweb and write them 
+    to 'beenames.csv'.
+
+"""
+bee_species_names = convert(Vector{String},unique(GBIF_bee_flower_interactions[!, "bumblebee"]))
+gbifbees = GBIF.taxon.(bee_species_names)
+filter!(!isnothing, gbifbees)
+beenames = DataFrame(species=[p.name for p in gbifbees])
+CSV.write(joinpath("cleandata", "beenames.csv"), beenames)
+
+
+
+
+
+
+ElkMeadowsInteractions = CSV.read(joinpath("rawdata", "ElkMeadowsBombus.csv"), DataFrame)
+
+names(ElkMeadowsInteractions)
+ElkMeadowsInteractions[!, "Ordinal day"]
[…]

### 2021-10-14 src/scripts/06_clipfastas.jl

@@ -1,0 +1,18 @@
+using BioSequences
+using FASTX
+
+r = open(FASTA.Reader, "./cleandata/UNALIGNED_CLEANED_plant_rbcL.fasta",)
+
+for record in r
+    name = string(identifier(record), " ", description(record))
+    recstr = sequence(record)
+    a = length(recstr) < 650 ? recstr : recstr[begin:650]
+
+    newrec = FASTA.Record(name, a)
+    w = FASTA.Writer(open("my-out.fasta", "a"))
+    write(w, newrec)
+    close(w)
+end
+
+
+close(r)

### 2021-10-14 src/scripts/trees.R

@@ -1,0 +1,23 @@
+
+library(phytools)
+
+setwd("/home/michael/papers/ms_bumblebees/src")
+
+read.tree("cleandata/CONSENSUS.nex")
+tr = read.tree("cleandata/ee_consensus.tree")
+
+plot(tr)
+nodelabels(tr$edge.length)
+
+
+
+setwd("/home/michael/papers/ms_bumblebees/src")
+
+tr = read.nexus("plants_con.tree")
+cliptr = read.nexus("clipped_consensus_tree_plants.tree")
+
+
+
+plot(tr, use.edge.length=FALSE)
+
+plot(cliptr)

### 2021-10-14 src/trees.R

@@ -1,20 +1,25 @@
-library(ape)
-library(ips)
+
 library(phytools)
 
-setwd("/home/michael/papers/ms_bumblebees/src")
+setwd("/home/michael/papers/ms_bumblebees/src/")
 
-read.tree("cleandata/CONSENSUS.nex")
-tr = read.tree("cleandata/ee_consensus.tree")
+df = read.csv("rawdata/bumblebee_interactions.csv")
+names(df)
 
-plot(tr)
-nodelabels(tr$edge.length)
+beetree = read.nexus("bee_consensus.tree")
+planttree = read.nexus("clipped_consensus.tree")
+
+
+df =read.csv("tmpmetaweb.csv")
+
+df = df[!is.na(df$plant),]
 
 
 
-setwd("/home/michael/papers/ms_bumblebees/src")
 
-tr = ips::read("inprog_plants.nex")
+dev.new(width = 15, height=12)
 
-plot(tr)
-nodelabels(tr$edge.length)
+
+co = cophylo(planttree,beetree, rotate=FALSE)
+plot(co)
+

### 2021-10-15 src/scripts/01_clean_data.jl
new concept

@@ -23,7 +23,7 @@ for row in 1:nrow(GBIF_bee_flower_interactions)
    push!(df_to_write.plant, plant)
 end
 
-CSV.write( "tmpmetaweb.csv",df_to_write,)
+CSV.write( "tmpmetaweb.csv",df_to_write)
 
 """
     Get the names of plant species from GBIF metaweb and write them 
@@ -48,31 +48,3 @@ gbifbees = GBIF.taxon.(bee_species_names)
 filter!(!isnothing, gbifbees)
 beenames = DataFrame(species=[p.name for p in gbifbees])
 CSV.write(joinpath("cleandata", "beenames.csv"), beenames)
-
-
-
-
-
-
-ElkMeadowsInteractions = CSV.read(joinpath("rawdata", "ElkMeadowsBombus.csv"), DataFrame)
-
-names(ElkMeadowsInteractions)
-ElkMeadowsInteractions[!, "Ordinal day"]
-ElkMeadowsInteractions[!, "Plot"]
-ElkMeadowsInteractions[!, "Insect species name"]
-ElkMeadowsInteractions[!, "Plant species name"]
-
-
-RMBL_phenology = CSV.read(joinpath("rawdata", "caradonna_rmbl_flowering_phenology_data_EDI.csv"), DataFrame)
-names(RMBL_phenology)
-RMBL_phenology[!, "plant"]
-
-
-RMBL_interactions = CSV.read(joinpath("rawdata", "caradonna_rmbl_interaction_networks_data_EDI.csv"), DataFrame)
-names(RMBL_interactions)
-RMBL_interactions[!, "plant"]
-RMBL_interactions[!, "pollinator"]
-RMBL_interactions[!, "interactions"]
-RMBL_interactions[!, "site"]
-RMBL_interactions[!, "year"]
-RMBL_interactions[!, "day_of_year"]

### 2021-10-15 src/scripts/03_bee_sdms.jl

@@ -1,4 +1,10 @@
+using DataFrames
+using DataFramesMeta
+using CSV
+using Shapefile
 
+
+using SimpleSDMLayers, GBIF, Plots
 
 
 speciesstrs =
@@ -53,15 +59,15 @@ function getplot(s)
     geoms = Shapefile.shapes(table)
 
 
-    plot(frame=:none, tickfont=4, xlim=(-109, -102), ylim=(37,41), size=(300,300))
-    plot!(elev, c=:Blues_9, colorbar=:none)
+    plot(frame=:none, tickfont=4, xlim=(-109, -102), ylim=(37,41), size=(500,500))
+    plot!(elev, c=:Greens_9, colorbar=:none)
     plot!(geoms, lc=:white, fa=0, lw=1)
     scatter!(
         longitudes(observations),
         latitudes(observations);
         lab="",
         c=:white,
-        msc=:orange,
+        msc=:dodgerblue,
         ms=3,
         alpha=0.5,
     )
@@ -69,6 +75,7 @@ function getplot(s)
 end
 
 
+bounds = (left=-109.6, right=-102.4, top=40.995, bottom=37.01 )
 
 plts = []
 
@@ -77,6 +84,8 @@ for s in specieslist
 end
 
 
+getplot(specieslist[1])
+
 plot(plts..., size=(2000,2000))
 
-savefig("occurrence_and_elevation.png")
+savefig("singleocc.png")

### 2021-10-15 src/scripts/field_data_overlap.jl

@@ -1,0 +1,46 @@
+using CSV, DataFrames
+
+
+
+"""
+    Julians Metaweb
+"""
+ElkMeadowsInteractions = CSV.read(joinpath("rawdata", "ElkMeadowsBombus.csv"), DataFrame)
+
+names(ElkMeadowsInteractions)
+ElkMeadowsInteractions[!, "Ordinal day"]
+ElkMeadowsInteractions[!, "Plot"]
+ElkMeadowsInteractions[!, "Insect species name"]
+ElkMeadowsInteractions[!, "Plant species name"]
+
+# split into species/genus
+
+
+unique(ElkMeadowsInteractions[!, "Plant species name"])
+unique(ElkMeadowsInteractions[!, "Insect species name"])
+# convert  Genus species -> genus_species
+
+
+"""
+    RMBL data
+"""
+
+RMBL_phenology = CSV.read(joinpath("rawdata", "caradonna_rmbl_flowering_phenology_data_EDI.csv"), DataFrame)
+names(RMBL_phenology)
+
+unique(RMBL_phenology[!, "plant"]) # 46
+
+RMBL_interactions = CSV.read(joinpath("rawdata", "caradonna_rmbl_interaction_networks_data_EDI.csv"), DataFrame)
+names(RMBL_interactions)
+
+
+
+
+unique(RMBL_interactions[!, "plant"])
+unique(RMBL_interactions[!, "pollinator"])
+
+
+RMBL_interactions[!, "interactions"]
+RMBL_interactions[!, "site"]
+RMBL_interactions[!, "year"]
+RMBL_interactions[!, "day_of_year"]

### 2021-10-24 src/notebooks/notebook.jl
bunch of noise

@@ -1,3 +1,84 @@
+### A Pluto.jl notebook ###
+# v0.16.3
+
+using Markdown
+using InteractiveUtils
+
+# This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
+macro bind(def, element)
+    quote
+        local el = $(esc(element))
+        global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : missing
+        el
+    end
+end
+
+# ╔═╡ e462b0b8-c21d-428b-b9dc-29b0014b6897
+begin 
+	using DataFrames
+	using Plots
+	using SimpleSDMLayers
+	using CSV
+	using Distributions
+end
+
+# ╔═╡ 5f966b24-4601-4055-b897-08c19b7575e4
+md"# Bumblebee metaweb niche embedding"
+
+# ╔═╡ dd397d2b-6126-47e9-b38c-daf62d9564f3
+md"## load packages"
+
+# ╔═╡ 48e7c1d0-e5e7-4203-ac36-b20fe6f90758
+
+
+# ╔═╡ ea536901-5296-4c4c-8d5c-9f7e03fdadf9
+md"## run"
+
+# ╔═╡ fc33f8b1-d32b-4ef9-85c7-44a335f48a80
+N, P = 1000, 0.2
+
+# ╔═╡ f07f2c06-cdda-4856-8bf3-04eb6ebde77e
+dist = NegativeBinomial(N, P)
+
+# ╔═╡ ea44df47-adec-45dc-8c3c-dfa5f41e7c27
+@bind n html"<input type=range>"
+
+# ╔═╡ 0e29c7e9-0c7d-4e39-8846-07a1cfb6fd01
+f(n) = rand(dist, n)
+
+# ╔═╡ dcf4c486-dd8d-4172-9528-61684e960fce
+begin
+	sample = f(n)
+end
+
+# ╔═╡ 3c761a33-8f28-4fd6-ae0d-66ce7004bf29
+
+
+# ╔═╡ f3eaba52-66a0-45e3-b243-f70a62614c00
+
+
+# ╔═╡ 5e9fc96a-ff6a-4fca-9feb-bbfff6f6e800
+
+
+# ╔═╡ 00000000-0000-0000-0000-000000000001
[…]

### 2021-10-24 src/scripts/07_occurence_elevation_dist.jl

@@ -1,0 +1,112 @@
+using DataFrames
+using DataFramesMeta
+using CSV
+using Shapefile
+
+
+using SimpleSDMLayers, GBIF, Plots
+
+bounds = (left=-109.6, right=-102.4, top=40.995, bottom=37.01 )
+
+
+beespecies = convert(Vector{String},
+    vec(CSV.read(joinpath("cleandata", "beenames.csv"), 
+        DataFrame).species)
+)
+
+beetaxa = GBIF.taxon.(beespecies)
+
+elev = convert(Float32, SimpleSDMPredictor(WorldClim, Elevation;  bounds...))
+
+pollinatorelevlist = []
+
+
+for tx in beetaxa
+    try 
+        observations = occurrences(
+            tx, 
+            "hasCoordinate" => "true",
+            "country" => "US",
+            "decimalLatitude" => (bounds.bottom, bounds.top),
+            "decimalLongitude" => (bounds.left, bounds.right),
+            "limit" => 10000
+        )
+
+        while length(observations) < size(observations)
+            occurrences!(observations)
+        end
+
+        presences = mask(elev, observations, Bool)
+        thiselevlist  = convert(Vector{Float32}, elev[keys(presences)])
+
+        pollinatorelevlist = vcat(pollinatorelevlist, thiselevlist)
+    catch 
+        @info "failed with $tx"
+    end
+end 
+
+
+pollplt = histogram(pollinatorelevlist, ylim=(0,3000), xlim=(1000, 3500), c=:orange, title="Pollinator GBIF occurrence records", label="GBIF obs", fa=0.3, frame=:box, legend=:outerright)
+xlabel!("elevation")
+ylabel!("count")
+
+plot!([2500, 3500], [1500, 1500], c=:forestgreen, ribbon=100, label="RMBL")
+plot!([2900, 3500], [2000, 2000], c=:dodgerblue, ribbon=100, label="Niwot")
+plot!([2600, 3500], [2500, 2500], c=:red, ribbon=100, label="Pikes Peak base to summit")
+ 
+
+savefig("elevs.png")
+
+
+
+# now the plants
+
+
+plantspecies = convert(Vector{String},
+    vec(CSV.read(joinpath("cleandata", "plantnames.csv"), 
+        DataFrame).species)
+)
+planttaxa = GBIF.taxon.(plantspecies, strict=false)
+
+
+plantelevlist = []
+
+
+for tx in planttaxa
+    try 
+        observations = occurrences(
+            tx, 
[…]

### 2021-10-24 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@329cfc0d89a50bb36d3f53610c8391098ced00ae 🚀
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@270724f5f8d4bcdefa83ffa78999c0b39db71d61 🚀
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@f5113fb8e21a8251c011203c8810d2429ccb1546 🚀
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@4b6befa1ada7bcfaa54843b7c68ca41519463b35 🚀

@@
 \thispagestyle{empty}
-{\Large\bfseries\sffamily Template to prepare preprints and manuscripts
-using markdown and github actions}
+{\Large\bfseries\sffamily Forecasting the spatio-temporal uncoupling of
+bumblebee-flower interaction networks}
 \vskip 5em
@@
 %
-\,\textsuperscript{1,2}
+\,\textsuperscript{1,2}\quad %
+\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
+%
+\,\textsuperscript{3,4,2}\quad %
+Paul\,CaraDonna%
+%
+\,\textsuperscript{5,6,‡}\quad %
+\href{https://orcid.org/0000-0002-2151-6693}{Dominique\,Caron}%
+%
+\,\textsuperscript{1,2}\quad %
+\href{https://orcid.org/0000-0002-6248-3007}{Philippe\,Desjardins-Proulx}%
+%
+\,\textsuperscript{3,2}\quad %
+\href{https://orcid.org/0000-0001-9019-0108}{Norma R.\,Forero-Muñoz}%
+%
+\,\textsuperscript{3,2}\quad %
+\href{https://orcid.org/0000-0001-6075-8081}{Andrew\,Gonzalez}%
+%
+\,\textsuperscript{1,2}\quad %
+\href{https://orcid.org/0000-0002-4498-7076}{Dominique\,Gravel}%
+%
+\,\textsuperscript{4,2}\quad %
+Jane E.\,Ogilvie%
+%
+\,\textsuperscript{5,‡}\quad %
+\href{https://orcid.org/0000-0002-6004-4027}{Laura\,Pollock}%
+%
+\,\textsuperscript{1,2}\quad %
+\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
+%
+\,\textsuperscript{3,2,‡}\quad %
+\href{https://orcid.org/0000-0001-6067-1349}{Tanya\,Strydom}%
+%
+\,\textsuperscript{3,2,‡}\quad %
+Julian\,Resasco%
+%
+\,\textsuperscript{7,‡}
 
 \textsuperscript{1}\,McGill University\quad \textsuperscript{2}\,Québec
-Centre for Biodiversity Sciences
+Centre for Biodiversity Sciences\quad \textsuperscript{3}\,Université de
+Montréal\quad \textsuperscript{4}\,Université de
+Sherbrooke\quad \textsuperscript{5}\,Rocky Mountain Biological
+Laboratory\quad \textsuperscript{6}\,Chicago Bontanic
+Garden\quad \textsuperscript{7}\,University of Colorado Boulder
+
+\textsuperscript{‡}\,These authors contributed equally to the work\\
 
@@
 
+\emph{title ideas}: Forecasting the spatio-temporal uncoupling of
+bumblebee-flower interaction networks
+
 \hypertarget{introduction}{%
@@
 
-This document is for brainstorming the Colorado bumblebee metaweb
-prediction project.
+Species interactions and climate change.
 
-\hypertarget{data}{%
-\section{1 Data}\label{data}}
+Two dimensions: spatial and temporal.
 
-The data consists of two parts, the field data collected at three
-stations across Colorado, and the GBIF metaweb data aggregated and
-cleaned by Julian R. and a student.
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\tightlist
+\item
+  Elevation gradients.
+\end{enumerate}
 
-\hypertarget{field-data}{%
-\subsection{1.1 Field data}\label{field-data}}
+\begin{itemize}
+\tightlist
+\item
+  dispersal capacity and range shifts
+\end{itemize}
 
-This data consists of nearly-daily records of visits between bee and
-flower species for the months August-October. Data is collected from
-three field sites: 1) Rocky Mountain Biological Lab (RMBL) 2) Niwot
-Ridge 3) Pikes Peak
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi})}
+\setcounter{enumi}{1}
+\tightlist
+\item
+  Phenological uncoupling {[}cite{]}.
+\end{enumerate}
 
-each with tens of plots each across an elevational gradient, collected
-for 7/4/3 summers total.
-
-\emph{To be determined}: specific number of plots per site and years per
-site
-
-\hypertarget{gbif-metaweb}{%
-\subsection{1.2 GBIF metaweb}\label{gbif-metaweb}}
-
-This data of a network of bee/flower species which have a record of both
-occurring on GBIF for locations at some spatial grain
-
-\emph{To be determined}: how does the scale of spatial aggregation
-affect properties of metaweb, how much taxonomic overlap is there with
-field data?---We have a lot of field data on interactions, but we can't
-validate predictions on taxa that aren't present in field data. As a
-result validation can only be done on interactions for which both
-species appear in field data.
+\begin{itemize}
+\tightlist
+\item
+  Abundance is a function of time in the year
+\end{itemize}
 
@@
 \section{Methods}\label{methods}}
+
+\hypertarget{data}{%
+\subsection{Data}\label{data}}
+
+\hypertarget{models}{%
+\subsection{Models}\label{models}}
+
+We denote the predicted probability of two species, \(i\) and \(j\),
+interacting a \(p_{ij}\). The outcome is here is to build a model \(f\),
+or rather a set of candidate models, that take \(i\) and \(j\) and
+inputs, and which potentially combine this with .features
+
+\[p_{ij} = f(i,j)\]
+
+\hypertarget{candidate-models}{%
+\subsubsection{Candidate models}\label{candidate-models}}
+
+\textbf{\emph{True Neutral}}:
+\(f(i,j) = \frac{1}{\sum_i \sum_j 1} = 1 / (P\cdot F)\)
+
+\textbf{\emph{Relative-abundance (interaction neutral)}}:
+\(f(i,j) = A_i A_j\) where \(A_x\) is the relative abundance of species
+\(x\).
+
+\textbf{\emph{Relative-abundance + environment-embedding}}:
+\(f(i,j) = g(i,j, E_i, E_j)\)
+
+\textbf{\emph{Relative-abundance + phylogeny-embedding}}: \$\$
+
+\textbf{\emph{Relative-abundance + environment-embedding +
+phylogeny-embedding}}
+
+\begin{figure}
+\hypertarget{fig:concept}{%
+\centering
+\includegraphics{./figures/concept_v2.png}
+\caption{todo}\label{fig:concept}
+}
+\end{figure}
+
+In gravel et al 2017
+\[P(X_{iy}, X_{jy}, L_{ijy} | E_y) = P(X_{iy},X_{jy}P(L_{ijy} | X_{iy}, X_{jy}, E_y)\]
+Then decompose probability of co-occurence as
+\[P(X_{iy}, X_{jy}) = P(X_{iy})P(X_{jy})\]
 
@@
 
+\hypertarget{acknowledgements}{%
+\subsection{Acknowledgements}\label{acknowledgements}}
+
 \hypertarget{references}{%

### 2021-10-24 preprint.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@329cfc0d89a50bb36d3f53610c8391098ced00ae 🚀
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@270724f5f8d4bcdefa83ffa78999c0b39db71d61 🚀
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@f5113fb8e21a8251c011203c8810d2429ccb1546 🚀
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@4b6befa1ada7bcfaa54843b7c68ca41519463b35 🚀

@@
 
-\noindent {\LARGE \textbf{\textsf{Template to prepare preprints and
-manuscripts using markdown and github actions}}}
+\noindent {\LARGE \textbf{\textsf{Forecasting the spatio-temporal
+uncoupling of bumblebee-flower interaction networks}}}
 
@@
 %
-\,\textsuperscript{1,2}
+\,\textsuperscript{1,2}, %
+\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
+%
+\,\textsuperscript{3,4,2}, %
+Paul\,CaraDonna%
+%
+\,\textsuperscript{5,6,‡}, %
+\href{https://orcid.org/0000-0002-2151-6693}{Dominique\,Caron}%
+%
+\,\textsuperscript{1,2}, %
+\href{https://orcid.org/0000-0002-6248-3007}{Philippe\,Desjardins-Proulx}%
+%
+\,\textsuperscript{3,2}, %
+\href{https://orcid.org/0000-0001-9019-0108}{Norma R.\,Forero-Muñoz}%
+%
+\,\textsuperscript{3,2}, %
+\href{https://orcid.org/0000-0001-6075-8081}{Andrew\,Gonzalez}%
+%
+\,\textsuperscript{1,2}, %
+\href{https://orcid.org/0000-0002-4498-7076}{Dominique\,Gravel}%
+%
+\,\textsuperscript{4,2}, %
+Jane E.\,Ogilvie%
+%
+\,\textsuperscript{5,‡}, %
+\href{https://orcid.org/0000-0002-6004-4027}{Laura\,Pollock}%
+%
+\,\textsuperscript{1,2}, %
+\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
+%
+\,\textsuperscript{3,2,‡}, %
+\href{https://orcid.org/0000-0001-6067-1349}{Tanya\,Strydom}%
+%
+\,\textsuperscript{3,2,‡}, %
+Julian\,Resasco%
+%
+\,\textsuperscript{7,‡}
 \vskip 1em
 \textsuperscript{1}\,McGill University; \textsuperscript{2}\,Québec
-Centre for Biodiversity Sciences\\
+Centre for Biodiversity Sciences; \textsuperscript{3}\,Université de
+Montréal; \textsuperscript{4}\,Université de
+Sherbrooke; \textsuperscript{5}\,Rocky Mountain Biological
+Laboratory; \textsuperscript{6}\,Chicago Bontanic
+Garden; \textsuperscript{7}\,University of Colorado Boulder\\
+\textsuperscript{‡}\,These authors contributed equally to the work\\
 \vskip 1em
@@
 {\small{\bfseries Keywords}:\par
-pandoc\\pandoc-crossref\\github actions\\}
+species interactions\\ecological
+forecasting\\pollinators\\bumbleebees\\network ecology\\}
 }

### 2021-10-24 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@81f4d8850cb6ac9d31f9412fdc64c14e79a3b03c 🚀
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@3e3fe34c3ae3b650fbde211b7860deca8b36e095 🚀

@@
 %
-\,\textsuperscript{5,6,‡}\quad %
+\,\textsuperscript{5,6}\quad %
 \href{https://orcid.org/0000-0002-2151-6693}{Dominique\,Caron}%
@@
 %
-\,\textsuperscript{5,‡}\quad %
+\,\textsuperscript{5}\quad %
 \href{https://orcid.org/0000-0002-6004-4027}{Laura\,Pollock}%
@@
 %
-\,\textsuperscript{3,2,‡}\quad %
+\,\textsuperscript{3,2}\quad %
 \href{https://orcid.org/0000-0001-6067-1349}{Tanya\,Strydom}%
 %
-\,\textsuperscript{3,2,‡}\quad %
+\,\textsuperscript{3,2}\quad %
 Julian\,Resasco%
 %
-\,\textsuperscript{7,‡}
+\,\textsuperscript{7}
 
@@
 Garden\quad \textsuperscript{7}\,University of Colorado Boulder
-
-\textsuperscript{‡}\,These authors contributed equally to the work\\
 
@@
 \item
+  range shifts in latitude context
+\item
+  apply this to elevational gradients
+\item
   dispersal capacity and range shifts
@@
 \item
-  Phenological uncoupling {[}cite{]}.
+  Phenological uncoupling (\textbf{Olesen2011MisFor?}).
 \end{enumerate}
@@
 
+In this paper we\ldots. combine data from a variety of sources: field
+data from several sites, crowd-sourced data (GBIF), and remotely-sensed
+data. to produce a \emph{spatially and temporally explict} metaweb of
+bumblebee-flower interactions across Colorado. We then estimate the
+change in spatial and temporal overlap over time using the CMIP6 climate
+consensus forecast (\textbf{Karger2017CliHig?}).
+
 \hypertarget{methods}{%
 \section{Methods}\label{methods}}
+
+\begin{figure}
+\hypertarget{fig:concept}{%
+\centering
+\includegraphics{./figures/concept_v2.png}
+\caption{todo}\label{fig:concept}
+}
+\end{figure}
 
@@
 
-\hypertarget{models}{%
-\subsection{Models}\label{models}}
+This project involves assembly and integration of data from a variety of
+(both structured and unstructured) sources. This data can be divided
+into four categories: field data, GBIF data, remote-sensing data, and
+phylogenetic data.
+
+\hypertarget{field-data}{%
+\subsubsection{Field data}\label{field-data}}
+
+The field data consists of: (1) a seven year data-set from Rocky
+Mountain Biological Laboratory, consisting of season-long interaction
+and phenology data six plots along an elevation gradient. (2) a similar
+six year data set from Elk Meadows, CO, and (3) a year across a large
+elevation gradient at Pikes Peak.
+
+Additional in-situ environmental sensors.
+
+The partitioning of this data into training, test, and validation sets
+if described in the \emph{Models} section.
+
+\hypertarget{gbif-data}{%
+\subsubsection{GBIF data}\label{gbif-data}}
+
+The data from Global Biodiversity Information Facility (GBIF) itself
+comes in two forms: (1) spatial records of bumblebee and flower records
+(2) sparsely available records of the plants a bee was observed on (TODO
+details from Julian).
+
+\hypertarget{remote-sensing-data}{%
+\subsubsection{Remote-sensing data}\label{remote-sensing-data}}
+
+The remote-sensing data consists of high-resolution LiDAR elevation data
+at 1 meter spatial resolution
+{[}(\textbf{NationalEcologicalObservatoryNetworkNEON2021EleLid?});{]},
+and daily 1km resolution precipitation and temperature from CHELSA
+(\textbf{Karger2021GloDai?}).
+
+\hypertarget{phylogenic-data}{%
+\subsubsection{Phylogenic data}\label{phylogenic-data}}
+
+The phylogenetic data consists of genomic barcodes available from NCBI
+GenBank.
+
+\hypertarget{a-spatiotemporally-explicit-predictive-metaweb-model}{%
+\subsection{A spatiotemporally explicit predictive metaweb
+model}\label{a-spatiotemporally-explicit-predictive-metaweb-model}}
+
+What does it mean for it to be ``spatiotemporally explicit?'' Well the
+formal definition of a metaweb is total species pool and
 
@@
 phylogeny-embedding}}
-
-\begin{figure}
-\hypertarget{fig:concept}{%
-\centering
-\includegraphics{./figures/concept_v2.png}
-\caption{todo}\label{fig:concept}
-}
-\end{figure}
 

### 2021-10-24 preprint.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@81f4d8850cb6ac9d31f9412fdc64c14e79a3b03c 🚀
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@3e3fe34c3ae3b650fbde211b7860deca8b36e095 🚀

@@
 %
-\,\textsuperscript{5,6,‡}, %
+\,\textsuperscript{5,6}, %
 \href{https://orcid.org/0000-0002-2151-6693}{Dominique\,Caron}%
@@
 %
-\,\textsuperscript{5,‡}, %
+\,\textsuperscript{5}, %
 \href{https://orcid.org/0000-0002-6004-4027}{Laura\,Pollock}%
@@
 %
-\,\textsuperscript{3,2,‡}, %
+\,\textsuperscript{3,2}, %
 \href{https://orcid.org/0000-0001-6067-1349}{Tanya\,Strydom}%
 %
-\,\textsuperscript{3,2,‡}, %
+\,\textsuperscript{3,2}, %
 Julian\,Resasco%
 %
-\,\textsuperscript{7,‡}
+\,\textsuperscript{7}
 \vskip 1em
@@
 Garden; \textsuperscript{7}\,University of Colorado Boulder\\
-\textsuperscript{‡}\,These authors contributed equally to the work\\
 \vskip 1em

### 2021-10-24 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@ae9a1cdc5f3d535fa0e5ab43ba94a49ee154d4c4 🚀

@@
 \item
-  Phenological uncoupling (\textbf{Olesen2011MisFor?}).
+  Phenological uncoupling (Olesen \emph{et al.} 2011).
 \end{enumerate}
@@
 change in spatial and temporal overlap over time using the CMIP6 climate
-consensus forecast (\textbf{Karger2017CliHig?}).
+consensus forecast (Karger \emph{et al.} 2017).
 
@@
 The remote-sensing data consists of high-resolution LiDAR elevation data
-at 1 meter spatial resolution
-{[}(\textbf{NationalEcologicalObservatoryNetworkNEON2021EleLid?});{]},
-and daily 1km resolution precipitation and temperature from CHELSA
-(\textbf{Karger2021GloDai?}).
+at 1 meter spatial resolution {[}(NEON) (2021);{]}, and daily 1km
+resolution precipitation and temperature from CHELSA (Karger \emph{et
+al.} 2021).
 
@@
 
-\hypertarget{a-predictive-model-to-make-spatially-explicit-network-prediction}{%
-\subsection{A predictive model to make spatially explicit network
-prediction}\label{a-predictive-model-to-make-spatially-explicit-network-prediction}}
+\hypertarget{model-fitting-and-validation}{%
+\subsection{Model fitting and
+validation}\label{model-fitting-and-validation}}
 
-The goal is two have two predictive models: interaction-predictor model
-and a distribution-predictor model (a la Strydom \& Catchen et al.~2021,
-figure 2).
+Models are implemented and fitted in Julia v1.6, using Turing.jl
+{[}cite{]}
 
-The interaction-predictor model, \(f_i(s_i,s_j, \theta_i)\) predicts
-interaction based on species-level features \((s_i, s_j)\), and is
-trained on the field-data.
+\hypertarget{training-test-validation-split-scheme}{%
+\subsubsection{Training-test-validation split
+scheme}\label{training-test-validation-split-scheme}}
 
-These features could include Phylogeny (to be determined: how available
-are genomes or trees for these species) Environment/Climate Traits (to
-be determined: what trait data is available, how annoying is it to
-clean) Time (only for the phenology model, see 3.2 and 3.3)
-
-The distribution-predictor model, \(f_s(s_i, \vec{x}, t)\) is trained on
-GBIF data to predict the occurrence of species with features si at a
-location in space x, and time t. Many options here. Here the species
-level features could be Climatic variables derived from remote sensing
-products. Co-occurence to make a JSDM Potentially weighted by phenology
-information from field data. Time (only for the phenology model, see 3.2
-and 3.3)
-
-\hypertarget{combining-distribution-predictor-and-interaction-predictor-models}{%
-\subsection{Combining distribution-predictor and interaction-predictor
-models}\label{combining-distribution-predictor-and-interaction-predictor-models}}
-
-Can split this into two based on how the distribution-predictor works.
-If \(f_s\) predicts co-occurrence, then draw the species pool first and
-predict interactions between the species in that pool. If \(f_s\) is a
-single-species SDM, get the occurrence probability for each species p\_s
-and compute the probability of observing interaction as function of the
-product of occ. prob.
+How do this? Do we remove sites entirely? Years entirely? Perhaps pikes
+peak would be best as a validation set as its only one year anyway and
+is a larger elevation gradient.
 
@@
 \hypertarget{references}{%
-\section{References}\label{references}}
+\section*{References}\label{references}}
+\addcontentsline{toc}{section}{References}
+
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\hypertarget{ref-Karger2017CliHig}{}%
+Karger, D.N., Conrad, O., Böhner, J., Kawohl, T., Kreft, H., Soria-Auza,
+R.W., \emph{et al.} (2017). Climatologies at high resolution for the
+earth's land surface areas. \emph{Scientific Data}, 4, 170122.
+
+\leavevmode\hypertarget{ref-Karger2021GloDai}{}%
+Karger, D.N., Wilson, A.M., Mahony, C., Zimmermann, N.E. \& Jetz, W.
+(2021). Global daily 1km land surface precipitation based on cloud
+cover-informed downscaling. \emph{arXiv:2012.10108 {[}physics{]}}.
+
+\leavevmode\hypertarget{ref-NationalEcologicalObservatoryNetworkNEON2021EleLid}{}%
+(NEON), N.E.O.N. (2021). Elevation - LiDAR (DP3.30024.001):
+RELEASE-2021.
+
+\leavevmode\hypertarget{ref-Olesen2011MisFor}{}%
+Olesen, J.M., Bascompte, J., Dupont, Y.L., Elberling, H., Rasmussen, C.
+\& Jordano, P. (2011). Missing and forbidden links in mutualistic
+networks. \emph{Proceedings of the Royal Society B: Biological
+Sciences}, 278, 725--732.
+
+\end{CSLReferences}
 

### 2021-10-24 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@27bd0a084fff06da484ea460e7d0c13e83eaac7e 🚀

--- 2021-10-24 draft.tex
@@
 \thispagestyle{empty}
-{\Large\bfseries\sffamily Forecasting the spatio-temporal uncoupling of
-bumblebee-flower interaction networks}
+{\Large\bfseries\sffamily Template to prepare preprints and manuscripts
+using markdown and github actions}
 \vskip 5em
@@
 %
-\,\textsuperscript{1,2}\quad %
-\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
-%
-\,\textsuperscript{3,4,2}\quad %
-Paul\,CaraDonna%
-%
-\,\textsuperscript{5,6,‡}\quad %
-\href{https://orcid.org/0000-0002-2151-6693}{Dominique\,Caron}%
-%
-\,\textsuperscript{1,2}\quad %
-\href{https://orcid.org/0000-0002-6248-3007}{Philippe\,Desjardins-Proulx}%
-%
-\,\textsuperscript{3,2}\quad %
-\href{https://orcid.org/0000-0001-9019-0108}{Norma R.\,Forero-Muñoz}%
-%
-\,\textsuperscript{3,2}\quad %
-\href{https://orcid.org/0000-0001-6075-8081}{Andrew\,Gonzalez}%
-%
-\,\textsuperscript{1,2}\quad %
-\href{https://orcid.org/0000-0002-4498-7076}{Dominique\,Gravel}%
-%
-\,\textsuperscript{4,2}\quad %
-Jane E.\,Ogilvie%
-%
-\,\textsuperscript{5,‡}\quad %
-\href{https://orcid.org/0000-0002-6004-4027}{Laura\,Pollock}%
-%
-\,\textsuperscript{1,2}\quad %
-\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
-%
-\,\textsuperscript{3,2,‡}\quad %
-\href{https://orcid.org/0000-0001-6067-1349}{Tanya\,Strydom}%
-%
-\,\textsuperscript{3,2,‡}\quad %
-Julian\,Resasco%
-%
-\,\textsuperscript{7,‡}
+\,\textsuperscript{1,2}
 
 \textsuperscript{1}\,McGill University\quad \textsuperscript{2}\,Québec
-Centre for Biodiversity Sciences\quad \textsuperscript{3}\,Université de
-Montréal\quad \textsuperscript{4}\,Université de
-Sherbrooke\quad \textsuperscript{5}\,Rocky Mountain Biological
-Laboratory\quad \textsuperscript{6}\,Chicago Bontanic
-Garden\quad \textsuperscript{7}\,University of Colorado Boulder
-
-\textsuperscript{‡}\,These authors contributed equally to the work\\
+Centre for Biodiversity Sciences
 

### 2021-10-24 preprint.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@27bd0a084fff06da484ea460e7d0c13e83eaac7e 🚀

--- 2021-10-24 preprint.tex
@@
 
-\noindent {\LARGE \textbf{\textsf{Forecasting the spatio-temporal
-uncoupling of bumblebee-flower interaction networks}}}
+\noindent {\LARGE \textbf{\textsf{Template to prepare preprints and
+manuscripts using markdown and github actions}}}
 
@@
 %
-\,\textsuperscript{1,2}, %
-\href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
-%
-\,\textsuperscript{3,4,2}, %
-Paul\,CaraDonna%
-%
-\,\textsuperscript{5,6,‡}, %
-\href{https://orcid.org/0000-0002-2151-6693}{Dominique\,Caron}%
-%
-\,\textsuperscript{1,2}, %
-\href{https://orcid.org/0000-0002-6248-3007}{Philippe\,Desjardins-Proulx}%
-%
-\,\textsuperscript{3,2}, %
-\href{https://orcid.org/0000-0001-9019-0108}{Norma R.\,Forero-Muñoz}%
-%
-\,\textsuperscript{3,2}, %
-\href{https://orcid.org/0000-0001-6075-8081}{Andrew\,Gonzalez}%
-%
-\,\textsuperscript{1,2}, %
-\href{https://orcid.org/0000-0002-4498-7076}{Dominique\,Gravel}%
-%
-\,\textsuperscript{4,2}, %
-Jane E.\,Ogilvie%
-%
-\,\textsuperscript{5,‡}, %
-\href{https://orcid.org/0000-0002-6004-4027}{Laura\,Pollock}%
-%
-\,\textsuperscript{1,2}, %
-\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
-%
-\,\textsuperscript{3,2,‡}, %
-\href{https://orcid.org/0000-0001-6067-1349}{Tanya\,Strydom}%
-%
-\,\textsuperscript{3,2,‡}, %
-Julian\,Resasco%
-%
-\,\textsuperscript{7,‡}
+\,\textsuperscript{1,2}
 \vskip 1em
 \textsuperscript{1}\,McGill University; \textsuperscript{2}\,Québec
-Centre for Biodiversity Sciences; \textsuperscript{3}\,Université de
-Montréal; \textsuperscript{4}\,Université de
-Sherbrooke; \textsuperscript{5}\,Rocky Mountain Biological
-Laboratory; \textsuperscript{6}\,Chicago Bontanic
-Garden; \textsuperscript{7}\,University of Colorado Boulder\\
-\textsuperscript{‡}\,These authors contributed equally to the work\\
+Centre for Biodiversity Sciences\\
 \vskip 1em
@@
 {\small{\bfseries Keywords}:\par
-species interactions\\ecological
-forecasting\\pollinators\\bumbleebees\\network ecology\\}
+pandoc\\pandoc-crossref\\github actions\\}
 }

### 2021-10-25 src/notebooks/notebook.jl
pca of env layers

@@ -4,15 +4,6 @@
 using Markdown
 using InteractiveUtils
 
-# This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
-macro bind(def, element)
-    quote
-        local el = $(esc(element))
-        global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : missing
-        el
-    end
-end
-
 # ╔═╡ e462b0b8-c21d-428b-b9dc-29b0014b6897
 begin 
 	using DataFrames
@@ -20,45 +11,136 @@ begin
 	using SimpleSDMLayers
 	using CSV
 	using Distributions
+	using MultivariateStats
+	ENV["RASTERDATASOURCES_PATH"] = "/home/michael/data/"
 end
 
 # ╔═╡ 5f966b24-4601-4055-b897-08c19b7575e4
 md"# Bumblebee metaweb niche embedding"
 
+# ╔═╡ 927d4315-c4ff-4f8f-8923-6e399f40b23d
+
+
 # ╔═╡ dd397d2b-6126-47e9-b38c-daf62d9564f3
-md"## load packages"
+md"#### 1 Load packages"
+
+# ╔═╡ ddcba724-30e0-404e-a072-a44708171ae7
+md"#### 2 Load occurrence maps"
 
 # ╔═╡ 48e7c1d0-e5e7-4203-ac36-b20fe6f90758
+begin 
+	bee_occurrence_dir_path = "/home/michael/papers/ms_bumblebees/src/cleandata/bee_occurrence/"
+	bee_occurrence_filenames = string.(bee_occurrence_dir_path, split(read(`ls -1v $bee_occurrence_dir_path`, String)))
+end
 
-
-# ╔═╡ ea536901-5296-4c4c-8d5c-9f7e03fdadf9
-md"## run"
-
-# ╔═╡ fc33f8b1-d32b-4ef9-85c7-44a335f48a80
-N, P = 1000, 0.2
-
-# ╔═╡ f07f2c06-cdda-4856-8bf3-04eb6ebde77e
-dist = NegativeBinomial(N, P)
[…]

### 2021-10-25 src/scripts/08_save_occurrence_records.jl

@@ -1,0 +1,55 @@
+using CSV, DataFrames
+using SimpleSDMLayers, GBIF, Plots
+
+bounds = (left=-109.6, right=-102.4, top=40.995, bottom=37.01)
+
+beespecies = convert(Vector{String},
+    vec(CSV.read(joinpath("cleandata", "beenames.csv"), 
+        DataFrame).species)
+)
+
+plants = convert(Vector{String},vec(CSV.read(joinpath("cleandata", "plantnames.csv"), DataFrame).species))
+
+planttaxa = GBIF.taxon.(plants, strict=false)
+beetaxa = GBIF.taxon.(beespecies)
+elev = convert(Float32, geotiff(SimpleSDMPredictor, joinpath("cleandata", "co_elev.tif")))
+
+
+spname(str) = string(split(str, " ")[1], "_", split(str," ")[2]) 
+
+function write_occurrence_tifs(taxalist, speciesnames, dirname)
+    for (i,tx) in enumerate(taxalist)
+        try 
+            observations = occurrences(
+                tx, 
+                "hasCoordinate" => "true",
+                "country" => "US",
+                "decimalLatitude" => (bounds.bottom, bounds.top),
+                "decimalLongitude" => (bounds.left, bounds.right),
+                "limit" => 10000
+            )
+
+            while length(observations) < size(observations)
+                occurrences!(observations)
+            end
+
+            presences = mask(elev, observations, Int32)
+
+            geotiff("cleandata/$dirname/$(spname(speciesnames[i])).tif", presences)
+        catch 
+            @info "failed with $tx"
+        end
+    end 
+
+end
+
+write_occurrence_tifs(planttaxa, plants, "plant_occurrence")
+
+
+
+layers = SimpleSDMPredictor(CHELSA, BioClim, 1:19; bounds...);
+
+
+for (i,envlayer) in enumerate(layers)
+    geotiff("cleandata/env_layers/$i.tif", envlayer)
+end 

### 2021-10-25 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@60079a1e76ef77faff90185f4192f4756f9e647b 🚀

--- 2021-10-24 draft.tex
@@
 
-\emph{title ideas}: Forecasting the spatio-temporal uncoupling of
-bumblebee-flower interaction networks
-
 \hypertarget{introduction}{%
 \section{Introduction}\label{introduction}}
+
+Earth's ecosystems are subject to rapid change due to both climate and
+land-use change (\textbf{cite?}). These sudden shifts in environment
+alter both the spatial and temporal distribution of species.
+
+Ecosystems are composed of interactions between species.
+
+Species vary in spacem but also
 
@@
 \item
-  apply this to elevational gradients
+  apply this to elevation gradients
 \item
@@
 
-The remote-sensing data consists of high-resolution LiDAR elevation data
-at 1 meter spatial resolution {[}(NEON) (2021);{]}, and daily 1km
-resolution precipitation and temperature from CHELSA (Karger \emph{et
-al.} 2021).
+The remote-sensing data consists of 15-arcsecond elevation
+data(\textbf{GMTED2020?}, cite), and daily 1km resolution precipitation
+and temperature from CHELSA (Karger \emph{et al.} 2021).
 
@@
 
-\leavevmode\hypertarget{ref-NationalEcologicalObservatoryNetworkNEON2021EleLid}{}%
-(NEON), N.E.O.N. (2021). Elevation - LiDAR (DP3.30024.001):
-RELEASE-2021.
-
 \leavevmode\hypertarget{ref-Olesen2011MisFor}{}%

### 2021-11-20 src/notebooks/notebook.jl
adding concept for ch 1 fig

@@ -1,1345 +1,0 @@
-### A Pluto.jl notebook ###
-# v0.16.3
-
-using Markdown
-using InteractiveUtils
-
-# ╔═╡ e462b0b8-c21d-428b-b9dc-29b0014b6897
-begin 
-	using DataFrames
-	using Plots
-	using SimpleSDMLayers
-	using CSV
-	using Distributions
-	using MultivariateStats
-	ENV["RASTERDATASOURCES_PATH"] = "/home/michael/data/"
-end
-
-# ╔═╡ 5f966b24-4601-4055-b897-08c19b7575e4
-md"# Bumblebee metaweb niche embedding"
-
-# ╔═╡ 927d4315-c4ff-4f8f-8923-6e399f40b23d
-
-
-# ╔═╡ dd397d2b-6126-47e9-b38c-daf62d9564f3
-md"#### 1 Load packages"
-
-# ╔═╡ ddcba724-30e0-404e-a072-a44708171ae7
-md"#### 2 Load occurrence maps"
-
-# ╔═╡ 48e7c1d0-e5e7-4203-ac36-b20fe6f90758
-begin 
-	bee_occurrence_dir_path = "/home/michael/papers/ms_bumblebees/src/cleandata/bee_occurrence/"
-	bee_occurrence_filenames = string.(bee_occurrence_dir_path, split(read(`ls -1v $bee_occurrence_dir_path`, String)))
-end
-
-# ╔═╡ a08fa15f-7c05-43c4-a4b8-7c73c7a49c23
-begin 
-	tifs = []
-	for f in bee_occurrence_filenames 
-		a = geotiff(SimpleSDMPredictor, f)
-		push!(tifs, a)
-	end
-end
-
-# ╔═╡ 3c761a33-8f28-4fd6-ae0d-66ce7004bf29
-md"#### Load environment data
-##### CHELSA data
-"
-
-# ╔═╡ 5e9fc96a-ff6a-4fca-9feb-bbfff6f6e800
-begin
-	bounds = (left=-109.6, right=-102.4, top=40.995, bottom=37.01)
-	layers = SimpleSDMPredictor(CHELSA, BioClim, 1:19; bounds...);
-	heatmap(layers[1].grid, dpi=1000)
-end
-
-# ╔═╡ 3a35ccd2-a632-411b-98b8-43afbc5d64a8
-md"###### Elevation data"
-
[…]

### 2021-11-20 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@393d0d8dc23e3dcd71818a02ea09831f5881e763 🚀

@@
 \,\textsuperscript{1,2}\quad %
+Paul\,CaraDonna%
+%
+\,\textsuperscript{3,4}\quad %
+Jane E.\,Ogilvie%
+%
+\,\textsuperscript{3}\quad %
 \href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
 %
-\,\textsuperscript{3,4,2}\quad %
-Paul\,CaraDonna%
-%
-\,\textsuperscript{5,6}\quad %
+\,\textsuperscript{5,6,2}\quad %
 \href{https://orcid.org/0000-0002-2151-6693}{Dominique\,Caron}%
@@
 %
-\,\textsuperscript{3,2}\quad %
+\,\textsuperscript{5,2}\quad %
 \href{https://orcid.org/0000-0001-9019-0108}{Norma R.\,Forero-Muñoz}%
 %
-\,\textsuperscript{3,2}\quad %
+\,\textsuperscript{5,2}\quad %
 \href{https://orcid.org/0000-0001-6075-8081}{Andrew\,Gonzalez}%
@@
 %
-\,\textsuperscript{4,2}\quad %
-Jane E.\,Ogilvie%
-%
-\,\textsuperscript{5}\quad %
+\,\textsuperscript{6,2}\quad %
 \href{https://orcid.org/0000-0002-6004-4027}{Laura\,Pollock}%
@@
 %
-\,\textsuperscript{3,2}\quad %
+\,\textsuperscript{5,2}\quad %
 \href{https://orcid.org/0000-0001-6067-1349}{Tanya\,Strydom}%
 %
-\,\textsuperscript{3,2}\quad %
+\,\textsuperscript{5,2}\quad %
 Julian\,Resasco%
@@
 \textsuperscript{1}\,McGill University\quad \textsuperscript{2}\,Québec
-Centre for Biodiversity Sciences\quad \textsuperscript{3}\,Université de
-Montréal\quad \textsuperscript{4}\,Université de
-Sherbrooke\quad \textsuperscript{5}\,Rocky Mountain Biological
-Laboratory\quad \textsuperscript{6}\,Chicago Bontanic
-Garden\quad \textsuperscript{7}\,University of Colorado Boulder
+Centre for Biodiversity Sciences\quad \textsuperscript{3}\,Rocky
+Mountain Biological Laboratory\quad \textsuperscript{4}\,Chicago
+Bontanic Garden\quad \textsuperscript{5}\,Université de
+Montréal\quad \textsuperscript{6}\,Université de
+Sherbrooke\quad \textsuperscript{7}\,University of Colorado Boulder
 
@@
 
-Species vary in spacem but also
+Main idea here: we have interaction information for some subset of the
+species pool, and good SDMs for a different subset of the species pool.
+There is some overlap in these species poolsHow do we combine this to
+predict: species interactions, uncertainty in interactions (which as
+increases indicates better use of sampling time).
 
@@
 
+This predictive model should not be used as definitive prediction:
+instead it reveals gaps in our sampling (where we have little confidence
+in predictions---see uncertainty figure). Iterative forecasting
+(\textbf{Diteze?}): use this model to guide sampling in the future to
+validate and update the model, etc.
+
 \hypertarget{acknowledgements}{%

### 2021-11-20 preprint.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@393d0d8dc23e3dcd71818a02ea09831f5881e763 🚀

@@
 \,\textsuperscript{1,2}, %
+Paul\,CaraDonna%
+%
+\,\textsuperscript{3,4}, %
+Jane E.\,Ogilvie%
+%
+\,\textsuperscript{3}, %
 \href{https://orcid.org/0000-0001-9051-0597}{Francis\,Banville}%
 %
-\,\textsuperscript{3,4,2}, %
-Paul\,CaraDonna%
-%
-\,\textsuperscript{5,6}, %
+\,\textsuperscript{5,6,2}, %
 \href{https://orcid.org/0000-0002-2151-6693}{Dominique\,Caron}%
@@
 %
-\,\textsuperscript{3,2}, %
+\,\textsuperscript{5,2}, %
 \href{https://orcid.org/0000-0001-9019-0108}{Norma R.\,Forero-Muñoz}%
 %
-\,\textsuperscript{3,2}, %
+\,\textsuperscript{5,2}, %
 \href{https://orcid.org/0000-0001-6075-8081}{Andrew\,Gonzalez}%
@@
 %
-\,\textsuperscript{4,2}, %
-Jane E.\,Ogilvie%
-%
-\,\textsuperscript{5}, %
+\,\textsuperscript{6,2}, %
 \href{https://orcid.org/0000-0002-6004-4027}{Laura\,Pollock}%
@@
 %
-\,\textsuperscript{3,2}, %
+\,\textsuperscript{5,2}, %
 \href{https://orcid.org/0000-0001-6067-1349}{Tanya\,Strydom}%
 %
-\,\textsuperscript{3,2}, %
+\,\textsuperscript{5,2}, %
 Julian\,Resasco%
@@
 \textsuperscript{1}\,McGill University; \textsuperscript{2}\,Québec
-Centre for Biodiversity Sciences; \textsuperscript{3}\,Université de
-Montréal; \textsuperscript{4}\,Université de
-Sherbrooke; \textsuperscript{5}\,Rocky Mountain Biological
-Laboratory; \textsuperscript{6}\,Chicago Bontanic
-Garden; \textsuperscript{7}\,University of Colorado Boulder\\
+Centre for Biodiversity Sciences; \textsuperscript{3}\,Rocky Mountain
+Biological Laboratory; \textsuperscript{4}\,Chicago Bontanic
+Garden; \textsuperscript{5}\,Université de
+Montréal; \textsuperscript{6}\,Université de
+Sherbrooke; \textsuperscript{7}\,University of Colorado Boulder\\
 \vskip 1em

### 2022-04-18 src/rawdata/bumblebeenetwork.R
moving to BumblebeeMetaweb repo

@@ -1,288 +1,0 @@
-# Bumblebee network project
-# J. Resasco
-setwd("/Users/julianresasco 1/Documents/Data/Bumblebee networks")
-
-library(reshape2)
-library(bipartite)
-library(igraph)
-library(vegan)
-
-intr <- read.csv("bumblebee_interactions.csv")
-plnt <- read.csv("plants.csv")
-bmbe <- read.csv("bmbl.bee.csv")
-elkb <- read.csv("ElkMeadowsBombus.csv")
-
-head(intr)
-head(plnt)
-head(bmbe)
-head(elkb)
-
-# check data for slight variations of variable names
-sort(unique(intr$plant.ackerfield))
-sort(unique(intr$species.plant))
-sort(unique(intr$bumblebee))
-
-# remove species
-intr <- subset(intr, intr$plant.ackerfield != "UNKNOWN SP UNKNOWN SP")
-intr <- subset(intr, intr$plant.ackerfield != "NA NA")
-intr <- subset(intr, intr$species.plant != "sp.")
-dim(intr)
-occ = rep(1, dim(intr)[1])
-intr <- cbind(intr, occ)
-
-# a useful function to make quantitative matrices binary
-quant2bin<-function(matr)
-{
-    ij<-which(matr!=0,arr.ind=T)
-    matrb<-matrix(0,dim(matr)[1],dim(matr)[2])
-    matrb[ij]<-1
-    return(matrb)
-}
-
-# build Colorado metaweb
-# make long data into plant x pollinator matrix
-comw <- acast(intr, plant.ackerfield~bumblebee, 
-                value.var="occ", fun.aggregate = sum)
-
-# plotweb visualization  
-plotweb(comw, method="normal",arrow="both",bor.col.interaction="grey", y.width.low=0.02, y.width.high=0.02, col.high="tomato", col.low="yellow green", high.lablength=20, low.lablength=20, text.rot = 90)
-
-
-# build subweb from a focal time and/or site 
-
-# select focal county
-county = "Boulder"
-
-# select focal elevation for Elk Meadow
-elevat.min = 9500
-elevat.max = 10000
-
-# select focal season
-#season.min = 
-#season.max = 
-
-# subset plants to focal site and elevation
-plant.sub <- subset(plnt, plnt$Boulder == 1)
[…]

### 2022-04-18 src/scripts/01_clean_data.jl

@@ -1,50 +1,0 @@
-using DataFrames
-using DataFramesMeta
-using CSV
-using Shapefile
-
-
-using SimpleSDMLayers, GBIF, Plots
-
-# each row is a species and columns are range data, and list of counties 
-GBIF_bee_occurrence = CSV.read(joinpath("rawdata", "bmbl.bee.csv"), DataFrame)
-
-# each row is an interaction
-GBIF_bee_flower_interactions = CSV.read(joinpath("rawdata", "bumblebee_interactions.csv"), DataFrame)
-names(GBIF_bee_flower_interactions)
-
-df_to_write = DataFrame(bee=[], plant=[])
-
-for row in 1:nrow(GBIF_bee_flower_interactions)
-   thisrow = GBIF_bee_flower_interactions[row, :]
-   bee, plant = thisrow["bumblebee"], thisrow["genus.plant"]
-
-   push!(df_to_write.bee, bee)
-   push!(df_to_write.plant, plant)
-end
-
-CSV.write( "tmpmetaweb.csv",df_to_write)
-
-"""
-    Get the names of plant species from GBIF metaweb and write them 
-    to 'plantnames.csv'.
-
-"""
-plant_full_species_names = convert(Vector{String},unique(GBIF_bee_flower_interactions[!, "plant.ackerfield"]))
-gbifplants = GBIF.taxon.(plant_full_species_names, strict=false)
-filter!(!isnothing, gbifplants)
-plantnames = DataFrame(species=[p.name for p in gbifplants])
-CSV.write(joinpath("cleandata", "plantnames.csv"), plantnames)
-
-
-
-"""
-    Get the names of bee species from GBIF metaweb and write them 
-    to 'beenames.csv'.
-
-"""
-bee_species_names = convert(Vector{String},unique(GBIF_bee_flower_interactions[!, "bumblebee"]))
-gbifbees = GBIF.taxon.(bee_species_names)
-filter!(!isnothing, gbifbees)
-beenames = DataFrame(species=[p.name for p in gbifbees])
-CSV.write(joinpath("cleandata", "beenames.csv"), beenames)

### 2022-04-18 src/scripts/02_plant_sdms.jl

@@ -1,58 +1,0 @@
-bounds = (left=-109.6, right=-102.4, top=40.995, bottom=37.01 )
-
-observations = []
-
-
-
-function getplantplot(observations, nm)
-    elev = convert(Float32, SimpleSDMPredictor(WorldClim, Elevation;  bounds...))
-
-    path = joinpath("rawdata", "colorado_counties","Colorado_County_Boundaries.shp")
-    table = Shapefile.Table(path)
-    geoms = Shapefile.shapes(table)
-
-
-    plot(frame=:none, tickfont=4, xlim=(-109, -102), ylim=(37,41), size=(300,300))
-    plot!(elev, c=:Blues_9, colorbar=:none)
-    plot!(geoms, lc=:white, fa=0, lw=1)
-    scatter!(
-        longitudes(observations),
-        latitudes(observations);
-        lab="",
-        c=:white,
-        msc=:orange,
-        ms=3,
-        alpha=0.5,
-    )
-    title!(nm)
-end
-
-
-
-for pl in gbifplants
-    try
-        occ= occurrences(
-            pl, 
-            "hasCoordinate" => "true",
-            "country" => "US",
-            "decimalLatitude" => (bounds.bottom, bounds.top),
-            "decimalLongitude" => (bounds.left, bounds.right),
-            "limit" => 300
-        )
-
-        push!(observations, occ)
-    catch e
-        @info "failed on $pl with $e"
-    end
-end
-
-plantplts = []
-
-for (i,obs) in enumerate(observations)
-    push!(plantplts, getplantplot(obs, gbifplants[i].name))
-end
-
-
-plot(plantplts..., size=(5100,5100))
-
-savefig("elplanto.png")

### 2022-04-18 src/scripts/03_bee_sdms.jl

@@ -1,91 +1,0 @@
-using DataFrames
-using DataFramesMeta
-using CSV
-using Shapefile
-
-
-using SimpleSDMLayers, GBIF, Plots
-
-
-speciesstrs =
-["Bombus appositus", 
-"Bombus auricomus",
-"Bombus balteatus",
-"Bombus bifarius",
-"Bombus californicus",
-"Bombus centralis",
-"Bombus fernaldae",
-"Bombus fervidus",
-"Bombus flavifrons",
-"Bombus fraternus",
-"Bombus frigidus",
-"Bombus griseocollis",
-"Bombus huntii",
-"Bombus insularis",
-"Bombus melanopygus",
-"Bombus mixtus",
-"Bombus morrisoni",
-"Bombus nevadensis",
-"Bombus occidentalis",
-"Bombus pensylvanicus",
-"Bombus rufocinctus",
-"Bombus suckleyi",
-"Bombus sylvicola",
-"Bombus variabilis"]
-
-specieslist = GBIF.taxon.(speciesstrs)
-
-function getplot(s)
-
-    observations = occurrences(
-        s, 
-        "hasCoordinate" => "true",
-        "country" => "US",
-        "decimalLatitude" => (bounds.bottom, bounds.top),
-        "decimalLongitude" => (bounds.left, bounds.right),
-        "limit" => 10000
-    )
-
-    size(observations) <= 0 && return
-
-    while length(observations) < size(observations)
-        occurrences!(observations)
-    end
-
-    elev = convert(Float32, SimpleSDMPredictor(WorldClim, Elevation;  bounds...))
-
-    path = joinpath("rawdata", "colorado_counties","Colorado_County_Boundaries.shp")
-    table = Shapefile.Table(path)
-    geoms = Shapefile.shapes(table)
-
-
-    plot(frame=:none, tickfont=4, xlim=(-109, -102), ylim=(37,41), size=(500,500))
-    plot!(elev, c=:Greens_9, colorbar=:none)
-    plot!(geoms, lc=:white, fa=0, lw=1)
-    scatter!(
-        longitudes(observations),
-        latitudes(observations);
-        lab="",
-        c=:white,
-        msc=:dodgerblue,
-        ms=3,
-        alpha=0.5,
-    )
-    title!(s.name)
-end
-
-
-bounds = (left=-109.6, right=-102.4, top=40.995, bottom=37.01 )
-
-plts = []
-
[…]

### 2022-04-18 src/scripts/04_genbank_query.jl

@@ -1,22 +1,0 @@
-using CSV, DataFrames
-
-
-bees = CSV.read(joinpath("cleandata", "beenames.csv"), DataFrame) # bees?
-
-plants = CSV.read(joinpath("cleandata", "plantnames.csv"), DataFrame)
-# format is 
-# "Bombus appositus"[Organism] OR "Bombus auricomus"[Organism] OR ... etc.
-
-function makequery(species)
-    query = "$(species[begin])[Organism] OR "
-
-    for s in species[2:end-1]
-        query = string(query, "$s [Organism] OR ")
-    end
-
-    query = string(query, "$(species[end])[Organism]")
-end
-
-
-
-makequery(plants.species)

### 2022-04-18 src/scripts/05_bee_tree.jl

@@ -1,9 +1,0 @@
-using Phylo
-using Plots
-
-ts = open(parsenewick, "cleandata/bee_consensus.tree")
-
-
-plot(ts)
-
-savefig("eltree.png")

### 2022-04-18 src/scripts/06_clipfastas.jl

@@ -1,18 +1,0 @@
-using BioSequences
-using FASTX
-
-r = open(FASTA.Reader, "./cleandata/UNALIGNED_CLEANED_plant_rbcL.fasta",)
-
-for record in r
-    name = string(identifier(record), " ", description(record))
-    recstr = sequence(record)
-    a = length(recstr) < 650 ? recstr : recstr[begin:650]
-
-    newrec = FASTA.Record(name, a)
-    w = FASTA.Writer(open("my-out.fasta", "a"))
-    write(w, newrec)
-    close(w)
-end
-
-
-close(r)

### 2022-04-18 src/scripts/07_occurence_elevation_dist.jl

@@ -1,112 +1,0 @@
-using DataFrames
-using DataFramesMeta
-using CSV
-using Shapefile
-
-
-using SimpleSDMLayers, GBIF, Plots
-
-bounds = (left=-109.6, right=-102.4, top=40.995, bottom=37.01 )
-
-
-beespecies = convert(Vector{String},
-    vec(CSV.read(joinpath("cleandata", "beenames.csv"), 
-        DataFrame).species)
-)
-
-beetaxa = GBIF.taxon.(beespecies)
-
-elev = convert(Float32, SimpleSDMPredictor(WorldClim, Elevation;  bounds...))
-
-pollinatorelevlist = []
-
-
-for tx in beetaxa
-    try 
-        observations = occurrences(
-            tx, 
-            "hasCoordinate" => "true",
-            "country" => "US",
-            "decimalLatitude" => (bounds.bottom, bounds.top),
-            "decimalLongitude" => (bounds.left, bounds.right),
-            "limit" => 10000
-        )
-
-        while length(observations) < size(observations)
-            occurrences!(observations)
-        end
-
-        presences = mask(elev, observations, Bool)
-        thiselevlist  = convert(Vector{Float32}, elev[keys(presences)])
-
-        pollinatorelevlist = vcat(pollinatorelevlist, thiselevlist)
-    catch 
-        @info "failed with $tx"
-    end
-end 
-
-
-pollplt = histogram(pollinatorelevlist, ylim=(0,3000), xlim=(1000, 3500), c=:orange, title="Pollinator GBIF occurrence records", label="GBIF obs", fa=0.3, frame=:box, legend=:outerright)
-xlabel!("elevation")
-ylabel!("count")
-
-plot!([2500, 3500], [1500, 1500], c=:forestgreen, ribbon=100, label="RMBL")
-plot!([2900, 3500], [2000, 2000], c=:dodgerblue, ribbon=100, label="Niwot")
-plot!([2600, 3500], [2500, 2500], c=:red, ribbon=100, label="Pikes Peak base to summit")
- 
-
-savefig("elevs.png")
-
-
-
-# now the plants
-
-
-plantspecies = convert(Vector{String},
-    vec(CSV.read(joinpath("cleandata", "plantnames.csv"), 
-        DataFrame).species)
-)
-planttaxa = GBIF.taxon.(plantspecies, strict=false)
-
-
-plantelevlist = []
-
-
-for tx in planttaxa
-    try 
-        observations = occurrences(
-            tx, 
[…]

### 2022-04-18 src/scripts/08_save_occurrence_records.jl

@@ -1,55 +1,0 @@
-using CSV, DataFrames
-using SimpleSDMLayers, GBIF, Plots
-
-bounds = (left=-109.6, right=-102.4, top=40.995, bottom=37.01)
-
-beespecies = convert(Vector{String},
-    vec(CSV.read(joinpath("cleandata", "beenames.csv"), 
-        DataFrame).species)
-)
-
-plants = convert(Vector{String},vec(CSV.read(joinpath("cleandata", "plantnames.csv"), DataFrame).species))
-
-planttaxa = GBIF.taxon.(plants, strict=false)
-beetaxa = GBIF.taxon.(beespecies)
-elev = convert(Float32, geotiff(SimpleSDMPredictor, joinpath("cleandata", "co_elev.tif")))
-
-
-spname(str) = string(split(str, " ")[1], "_", split(str," ")[2]) 
-
-function write_occurrence_tifs(taxalist, speciesnames, dirname)
-    for (i,tx) in enumerate(taxalist)
-        try 
-            observations = occurrences(
-                tx, 
-                "hasCoordinate" => "true",
-                "country" => "US",
-                "decimalLatitude" => (bounds.bottom, bounds.top),
-                "decimalLongitude" => (bounds.left, bounds.right),
-                "limit" => 10000
-            )
-
-            while length(observations) < size(observations)
-                occurrences!(observations)
-            end
-
-            presences = mask(elev, observations, Int32)
-
-            geotiff("cleandata/$dirname/$(spname(speciesnames[i])).tif", presences)
-        catch 
-            @info "failed with $tx"
-        end
-    end 
-
-end
-
-write_occurrence_tifs(planttaxa, plants, "plant_occurrence")
-
-
-
-layers = SimpleSDMPredictor(CHELSA, BioClim, 1:19; bounds...);
-
-
-for (i,envlayer) in enumerate(layers)
-    geotiff("cleandata/env_layers/$i.tif", envlayer)
-end 

### 2022-04-18 src/scripts/field_data_overlap.jl

@@ -1,46 +1,0 @@
-using CSV, DataFrames
-
-
-
-"""
-    Julians Metaweb
-"""
-ElkMeadowsInteractions = CSV.read(joinpath("rawdata", "ElkMeadowsBombus.csv"), DataFrame)
-
-names(ElkMeadowsInteractions)
-ElkMeadowsInteractions[!, "Ordinal day"]
-ElkMeadowsInteractions[!, "Plot"]
-ElkMeadowsInteractions[!, "Insect species name"]
-ElkMeadowsInteractions[!, "Plant species name"]
-
-# split into species/genus
-
-
-unique(ElkMeadowsInteractions[!, "Plant species name"])
-unique(ElkMeadowsInteractions[!, "Insect species name"])
-# convert  Genus species -> genus_species
-
-
-"""
-    RMBL data
-"""
-
-RMBL_phenology = CSV.read(joinpath("rawdata", "caradonna_rmbl_flowering_phenology_data_EDI.csv"), DataFrame)
-names(RMBL_phenology)
-
-unique(RMBL_phenology[!, "plant"]) # 46
-
-RMBL_interactions = CSV.read(joinpath("rawdata", "caradonna_rmbl_interaction_networks_data_EDI.csv"), DataFrame)
-names(RMBL_interactions)
-
-
-
-
-unique(RMBL_interactions[!, "plant"])
-unique(RMBL_interactions[!, "pollinator"])
-
-
-RMBL_interactions[!, "interactions"]
-RMBL_interactions[!, "site"]
-RMBL_interactions[!, "year"]
-RMBL_interactions[!, "day_of_year"]

### 2022-04-18 src/scripts/trees.R

@@ -1,23 +1,0 @@
-
-library(phytools)
-
-setwd("/home/michael/papers/ms_bumblebees/src")
-
-read.tree("cleandata/CONSENSUS.nex")
-tr = read.tree("cleandata/ee_consensus.tree")
-
-plot(tr)
-nodelabels(tr$edge.length)
-
-
-
-setwd("/home/michael/papers/ms_bumblebees/src")
-
-tr = read.nexus("plants_con.tree")
-cliptr = read.nexus("clipped_consensus_tree_plants.tree")
-
-
-
-plot(tr, use.edge.length=FALSE)
-
-plot(cliptr)

### 2022-04-18 src/trees.R

@@ -1,25 +1,0 @@
-
-library(phytools)
-
-setwd("/home/michael/papers/ms_bumblebees/src/")
-
-df = read.csv("rawdata/bumblebee_interactions.csv")
-names(df)
-
-beetree = read.nexus("bee_consensus.tree")
-planttree = read.nexus("clipped_consensus.tree")
-
-
-df =read.csv("tmpmetaweb.csv")
-
-df = df[!is.na(df$plant),]
-
-
-
-
-dev.new(width = 15, height=12)
-
-
-co = cophylo(planttree,beetree, rotate=FALSE)
-plot(co)
-

### 2022-04-18 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@c76a7e0665deb15a003729157cf1313d9efbce37 🚀

@@
 species pool, and good SDMs for a different subset of the species pool.
-There is some overlap in these species poolsHow do we combine this to
+There is some overlap in these species pools. How do we combine this to
 predict: species interactions, uncertainty in interactions (which as
@@
 \item
-  Phenological uncoupling (Olesen \emph{et al.} 2011).
+  Phenological and spatial uncoupling (Olesen \emph{et al.} 2011).
 \end{enumerate}

### 2022-05-05 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@dd5224f1675ce6f10387cfdb6fd4426c85ed19d2 🚀

--- 2021-11-20 draft.tex
@@
 
+\hypertarget{abstract}{%
+\subsection{Abstract}\label{abstract}}
+
+Using a data set of {[}DESCRIBE EACH DATASET IN A NICE WAY{]}, we
+predict a spatiotemporally explicit metaweb of interactions between
+bumblebees (\emph{Bombus}) and wildflowers (within \emph{find clade}).
+We integrate this data with crowdsourced occurrence data and climate
+data to {[}best paint the picture of the Colorado bumblebee-plant
+metaweb{]}. Using temporal climate data, we forecast how the
+spatiotemporal overlap of interacting species will change under proposed
+climate scenarios. We use this to estimate what interactions between
+bees and plants need the most attention to prevent the spatiotemporal
+decoupling of an interactions from threatening ecosystem functioning or
+the persistence of a species.
+
 \hypertarget{introduction}{%
 \section{Introduction}\label{introduction}}
-
-Earth's ecosystems are subject to rapid change due to both climate and
-land-use change (\textbf{cite?}). These sudden shifts in environment
-alter both the spatial and temporal distribution of species.
-
-Ecosystems are composed of interactions between species.
-
-Main idea here: we have interaction information for some subset of the
-species pool, and good SDMs for a different subset of the species pool.
-There is some overlap in these species poolsHow do we combine this to
-predict: species interactions, uncertainty in interactions (which as
-increases indicates better use of sampling time).
-
-Species interactions and climate change.
-
-Two dimensions: spatial and temporal.
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi})}
-\tightlist
-\item
-  Elevation gradients.
-\end{enumerate}
 
@@
 \item
-  range shifts in latitude context
+  We estimate the Colorado bumblebee/wild-flower pollination metaweb
+  using network embedding.
 \item
-  apply this to elevation gradients
+  Then decompose into spatial and temporally explicit network
+  predictions
 \item
-  dispersal capacity and range shifts
+  Finally suggest a priority of sampling to improve our understanding of
+  this system.
 \end{itemize}
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi})}
-\setcounter{enumi}{1}
-\tightlist
-\item
-  Phenological uncoupling (Olesen \emph{et al.} 2011).
-\end{enumerate}
-
-\begin{itemize}
-\tightlist
-\item
-  Abundance is a function of time in the year
-\end{itemize}
-
-In this paper we\ldots. combine data from a variety of sources: field
-data from several sites, crowd-sourced data (GBIF), and remotely-sensed
-data. to produce a \emph{spatially and temporally explict} metaweb of
-bumblebee-flower interactions across Colorado. We then estimate the
-change in spatial and temporal overlap over time using the CMIP6 climate
-consensus forecast (Karger \emph{et al.} 2017).
+\hypertarget{data}{%
+\section{Data}\label{data}}
 
@@
 
-\begin{figure}
-\hypertarget{fig:concept}{%
-\centering
-\includegraphics{./figures/concept_v2.png}
-\caption{todo}\label{fig:concept}
-}
-\end{figure}
+\textbf{\emph{Concept Fig}}
 
-\hypertarget{data}{%
-\subsection{Data}\label{data}}
+\hypertarget{metaweb-model}{%
+\section{Metaweb Model}\label{metaweb-model}}
 
-This project involves assembly and integration of data from a variety of
-(both structured and unstructured) sources. This data can be divided
-into four categories: field data, GBIF data, remote-sensing data, and
-phylogenetic data.
+\hypertarget{phylogeny-construction}{%
+\subsection{Phylogeny Construction}\label{phylogeny-construction}}
 
-\hypertarget{field-data}{%
-\subsubsection{Field data}\label{field-data}}
+\hypertarget{feature-embedding}{%
+\subsection{Feature Embedding}\label{feature-embedding}}
 
-The field data consists of: (1) a seven year data-set from Rocky
-Mountain Biological Laboratory, consisting of season-long interaction
-and phenology data six plots along an elevation gradient. (2) a similar
-six year data set from Elk Meadows, CO, and (3) a year across a large
-elevation gradient at Pikes Peak.
+\hypertarget{relative-abundance}{%
+\subsubsection{Relative Abundance}\label{relative-abundance}}
 
-Additional in-situ environmental sensors.
+\hypertarget{phylogenetic-features}{%
+\subsubsection{Phylogenetic features}\label{phylogenetic-features}}
 
-The partitioning of this data into training, test, and validation sets
-if described in the \emph{Models} section.
+\hypertarget{environmental-niche-features}{%
+\subsubsection{Environmental niche
+features}\label{environmental-niche-features}}
 
-\hypertarget{gbif-data}{%
-\subsubsection{GBIF data}\label{gbif-data}}
+\hypertarget{temporal-niche-features}{%
+\subsubsection{Temporal niche features}\label{temporal-niche-features}}
 
-The data from Global Biodiversity Information Facility (GBIF) itself
-comes in two forms: (1) spatial records of bumblebee and flower records
-(2) sparsely available records of the plants a bee was observed on (TODO
-details from Julian).
+\hypertarget{metaweb-model-fitting-and-validation}{%
+\subsection{Metaweb Model Fitting and
+Validation}\label{metaweb-model-fitting-and-validation}}
 
-\hypertarget{remote-sensing-data}{%
-\subsubsection{Remote-sensing data}\label{remote-sensing-data}}
+\textbf{\emph{Figure 2: Model Fit Figure}}
+\includegraphics{./figures/PR_ROC.png} \# Spatiotemporally Explicit
+Networks
 
-The remote-sensing data consists of 15-arcsecond elevation
-data(\textbf{GMTED2020?}, cite), and daily 1km resolution precipitation
-and temperature from CHELSA (Karger \emph{et al.} 2021).
+Now that we have a metaweb\ldots..
 
-\hypertarget{phylogenic-data}{%
-\subsubsection{Phylogenic data}\label{phylogenic-data}}
+\textbf{\emph{Figure 3: Maps over time figure and Prob(Connectance)
+vs.~Month figure }}
 
-The phylogenetic data consists of genomic barcodes available from NCBI
-GenBank.
+\hypertarget{sampling-prioiritization}{%
+\section{Sampling Prioiritization}\label{sampling-prioiritization}}
 
-\hypertarget{a-spatiotemporally-explicit-predictive-metaweb-model}{%
-\subsection{A spatiotemporally explicit predictive metaweb
-model}\label{a-spatiotemporally-explicit-predictive-metaweb-model}}
-
-What does it mean for it to be ``spatiotemporally explicit?'' Well the
-formal definition of a metaweb is total species pool and
-
-We denote the predicted probability of two species, \(i\) and \(j\),
-interacting a \(p_{ij}\). The outcome is here is to build a model \(f\),
-or rather a set of candidate models, that take \(i\) and \(j\) and
-inputs, and which potentially combine this with .features
-
-\[p_{ij} = f(i,j)\]
-
-\hypertarget{candidate-models}{%
-\subsubsection{Candidate models}\label{candidate-models}}
-
-\textbf{\emph{True Neutral}}:
-\(f(i,j) = \frac{1}{\sum_i \sum_j 1} = 1 / (P\cdot F)\)
-
-\textbf{\emph{Relative-abundance (interaction neutral)}}:
-\(f(i,j) = A_i A_j\) where \(A_x\) is the relative abundance of species
-\(x\).
-
-\textbf{\emph{Relative-abundance + environment-embedding}}:
-\(f(i,j) = g(i,j, E_i, E_j)\)
-
-\textbf{\emph{Relative-abundance + phylogeny-embedding}}: \$\$
-
-\textbf{\emph{Relative-abundance + environment-embedding +
-phylogeny-embedding}}
-
-In gravel et al 2017
-\[P(X_{iy}, X_{jy}, L_{ijy} | E_y) = P(X_{iy},X_{jy}P(L_{ijy} | X_{iy}, X_{jy}, E_y)\]
-Then decompose probability of co-occurence as
-\[P(X_{iy}, X_{jy}) = P(X_{iy})P(X_{jy})\]
-
-\hypertarget{model-fitting-and-validation}{%
-\subsection{Model fitting and
-validation}\label{model-fitting-and-validation}}
-
-Models are implemented and fitted in Julia v1.6, using Turing.jl
-{[}cite{]}
-
-\hypertarget{training-test-validation-split-scheme}{%
-\subsubsection{Training-test-validation split
-scheme}\label{training-test-validation-split-scheme}}
-
-How do this? Do we remove sites entirely? Years entirely? Perhaps pikes
-peak would be best as a validation set as its only one year anyway and
-is a larger elevation gradient.
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-After comparing different combinations of features/model structures and
-finding the `best' performing model on validation data.
-
-\hypertarget{figure-one-spatial-species-pool-and-network-prediction}{%
-\subsection{Figure one: spatial species pool and network
-prediction}\label{figure-one-spatial-species-pool-and-network-prediction}}
-
-Figure that is two panels: a map of total species richness and a map of
-network properties across Colorado. This model doesn't consider time,
-only other predictors.
-
-\hypertarget{figure-two-phenology}{%
-\subsection{Figure two: Phenology}\label{figure-two-phenology}}
-
-Same as figure one but consists of maps but at different times of the
-year (e.g. March, June, August) and uses both an interaction-predictor
-and distribution-predictor that incorporate time into predictions
-
-\hypertarget{figure-three-climate}{%
-\subsection{Figure three: Climate}\label{figure-three-climate}}
-
-Much as climate change has shifted temperature gradients to get warmer
-toward the poles, it has also moved temperature gradients up in
-elevation.
-
-We can get a CMIP6 forecast of temperature and precipitation, and then
-predict how many observed interactions in the field data will no longer
-have their composing species' distributions overlap. Decompose temporal
-component of overlap from spatial component.
+\textbf{\emph{Figure 4: Uncertainty and sampling priority map}}
 
@@
 
-This predictive model should not be used as definitive prediction:
-instead it reveals gaps in our sampling (where we have little confidence
-in predictions---see uncertainty figure). Iterative forecasting
-(\textbf{Diteze?}): use this model to guide sampling in the future to
-validate and update the model, etc.
-
-\hypertarget{acknowledgements}{%
-\subsection{Acknowledgements}\label{acknowledgements}}
-
-\hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-Karger2017CliHig}{}%
-Karger, D.N., Conrad, O., Böhner, J., Kawohl, T., Kreft, H., Soria-Auza,
-R.W., \emph{et al.} (2017). Climatologies at high resolution for the
-earth's land surface areas. \emph{Scientific Data}, 4, 170122.
-
-\leavevmode\hypertarget{ref-Karger2021GloDai}{}%
-Karger, D.N., Wilson, A.M., Mahony, C., Zimmermann, N.E. \& Jetz, W.
-(2021). Global daily 1km land surface precipitation based on cloud
-cover-informed downscaling. \emph{arXiv:2012.10108 {[}physics{]}}.
-
-\leavevmode\hypertarget{ref-Olesen2011MisFor}{}%
-Olesen, J.M., Bascompte, J., Dupont, Y.L., Elberling, H., Rasmussen, C.
-\& Jordano, P. (2011). Missing and forbidden links in mutualistic
-networks. \emph{Proceedings of the Royal Society B: Biological
-Sciences}, 278, 725--732.
-
-\end{CSLReferences}
-
 \end{document}

### 2022-05-06 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@4dfeb7848376a8e014f73bc4f73aa468a2264cde 🚀

@@
 
-\begin{itemize}
-\tightlist
-\item
-  We estimate the Colorado bumblebee/wild-flower pollination metaweb
-  using network embedding.
-\item
-  Then decompose into spatial and temporally explicit network
-  predictions
-\item
-  Finally suggest a priority of sampling to improve our understanding of
-  this system.
-\end{itemize}
+Species interactions are important. It is ultimately interactions
+between individuals of different species that drive the structure,
+dynamics, and persistence of ecosystems, and the abundance and diversity
+of the species within them. Plant-pollinator interactions specifically
+drive the function and persistence of ``architecture of biodiversity''
+(Bascompte \& Jordano 2007). However, we are far from a robust
+understanding of plant-pollinator networks is.
+
+In this paper, we combine several datasets, each spanning several years,
+to produce spatially and temporally explicit predictions of
+\emph{Bombus} plant-pollinator interactions across the state of
+Colorado.
+
+We do this in two parts: (1) metaweb prediction and (2) conditioning our
+metaweb prediction on co-occurrence probability.
+
+First, we build a model to predict the metaweb---the network of
+\emph{all} interactions, aggregated across all times and spatial
+locations---of \emph{Bombus} and wildflower species across Colorado.
+(Why do this? The metaweb is more predictable than local interactions.)
+We do this using network embedding (\textbf{cite?}). Network embedding
+takes each node in the network (either a bumblebee or a wildflower) and
+represents it in a latent \(n\) dimensional space. Combination of
+running models on Temporal niche (T), Phylogenetic niche (P),
+Environmental niche (E), and relative abundance in community (RA).
+
+Second, we then use this metaweb to predict the structure of networks at
+specific locations and times of year (Gravel \emph{et al.} 2019).
+
+Finally we suggest a map of sampling priority, which suggests the
+locations to sample that will best improve our understanding of the
+Colorado \emph{Bombus} pollination metaweb.
 
@@
 \section{Data}\label{data}}
+
+We use three separate datasets to estimate the Colorado \emph{Bombus}
+metaweb.
 
@@
 \textbf{\emph{Figure 2: Model Fit Figure}}
-\includegraphics{./figures/PR_ROC.png} \# Spatiotemporally Explicit
-Networks
+\includegraphics{./figures/PR_ROC.png}
+
+\hypertarget{spatiotemporally-explicit-networks}{%
+\section{Spatiotemporally Explicit
+Networks}\label{spatiotemporally-explicit-networks}}
 
@@
 \hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
+\section*{Discussion}\label{discussion}}
+\addcontentsline{toc}{section}{Discussion}
+
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\hypertarget{ref-Bascompte2007PlaMut}{}%
+Bascompte, J. \& Jordano, P. (2007). Plant-Animal Mutualistic Networks:
+The Architecture of Biodiversity. \emph{Annual Review of Ecology,
+Evolution, and Systematics}, 38, 567--593.
+
+\leavevmode\hypertarget{ref-Gravel2019BriElt}{}%
+Gravel, D., Baiser, B., Dunne, J.A., Kopelke, J.-P., Martinez, N.D.,
+Nyman, T., \emph{et al.} (2019). Bringing Elton and Grinnell together: A
+quantitative framework to represent the biogeography of ecological
+interaction networks. \emph{Ecography}, 42, 401--415.
+
+\end{CSLReferences}
 

### 2022-05-06 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@32d815466d82b076cbea6971b274867eee4da2a9 🚀

@@
 \thispagestyle{empty}
-{\Large\bfseries\sffamily Forecasting the spatio-temporal uncoupling of
-bumblebee-flower interaction networks}
+{\Large\bfseries\sffamily Building a better metaweb: predicting
+spatially and temporally explicit alpine plant-pollinator interaction
+networks}
 \vskip 5em
@@
 %
-\,\textsuperscript{5,6,2}\quad %
+\,\textsuperscript{3}\quad %
 \href{https://orcid.org/0000-0002-2151-6693}{Dominique\,Caron}%
@@
 \,\textsuperscript{5,2}\quad %
-\href{https://orcid.org/0000-0001-6075-8081}{Andrew\,Gonzalez}%
-%
-\,\textsuperscript{1,2}\quad %
 \href{https://orcid.org/0000-0002-4498-7076}{Dominique\,Gravel}%
@@
 \,\textsuperscript{1,2}\quad %
-\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
+\href{https://orcid.org/0000-0001-6067-1349}{Tanya\,Strydom}%
 %
 \,\textsuperscript{5,2}\quad %
-\href{https://orcid.org/0000-0001-6067-1349}{Tanya\,Strydom}%
+\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
 %
@@
 %
-\,\textsuperscript{7}
+\,\textsuperscript{7}\quad %
+\href{https://orcid.org/0000-0001-6075-8081}{Andrew\,Gonzalez}%
+%
+\,\textsuperscript{1,2}
 
@@
 (Bascompte \& Jordano 2007). However, we are far from a robust
-understanding of plant-pollinator networks is.
-
-In this paper, we combine several datasets, each spanning several years,
-to produce spatially and temporally explicit predictions of
-\emph{Bombus} plant-pollinator interactions across the state of
-Colorado.
+understanding of plant-pollinator networks. This is because sampling
+interactions is costly. Interactions vary in space and time (Poisot
+\emph{et al.} 2015)---particularlly relevent in this system {[}Paul
+phenology cite{]}. This is why there is interest in using models to
+predict interactions from sparse data (\textbf{Strydom2021?}). In this
+paper, we combine several datasets, each spanning several years, to
+produce spatially and temporally explicit predictions of the bumblebee
+(genus \emph{Bombus}) and wildflower pollination network across the
+state of Colorado.
 
 We do this in two parts: (1) metaweb prediction and (2) conditioning our
-metaweb prediction on co-occurrence probability.
-
-First, we build a model to predict the metaweb---the network of
-\emph{all} interactions, aggregated across all times and spatial
-locations---of \emph{Bombus} and wildflower species across Colorado.
-(Why do this? The metaweb is more predictable than local interactions.)
-We do this using network embedding (\textbf{cite?}). Network embedding
-takes each node in the network (either a bumblebee or a wildflower) and
-represents it in a latent \(n\) dimensional space. Combination of
-running models on Temporal niche (T), Phylogenetic niche (P),
-Environmental niche (E), and relative abundance in community (RA).
+metaweb prediction on co-occurrence probability. First, we build a model
+to predict the metaweb---the network of \emph{all} interactions,
+aggregated across all times and spatial locations---of \emph{Bombus} and
+wildflower species across Colorado. (Why do this? The metaweb is more
+predictable than local interactions.) We do this using network embedding
+(\textbf{cite?}). Network embedding takes each node in the network
+(either a bumblebee or a wildflower) and represents it in a latent \(n\)
+dimensional space. Combination of running models on Temporal niche (T),
+Phylogenetic niche (P), Environmental niche (E), and relative abundance
+in community (RA).
 
@@
 specific locations and times of year (Gravel \emph{et al.} 2019).
-
 Finally we suggest a map of sampling priority, which suggests the
@@
 
+Why is this good for science, what does this contribute to our
+understanding of plant-pollinator ints, networks, Bombus, predictive
+models, etc., and how can these results be useful.
+
 \hypertarget{data}{%
@@
 
-We use three separate datasets to estimate the Colorado \emph{Bombus}
-metaweb.
+We use three separate field datasets to estimate the Colorado
+\emph{Bombus} metaweb.
 
@@
 
-\textbf{\emph{Figure 2: Model Fit Figure}}
+\begin{figure}
+\centering
 \includegraphics{./figures/PR_ROC.png}
+\caption{todo}
+\end{figure}
 
@@
 \textbf{\emph{Figure 3: Maps over time figure and Prob(Connectance)
-vs.~Month figure }}
+vs.~Month figure}}
 
@@
 
+\leavevmode\hypertarget{ref-Poisot2015SpeWhy}{}%
+Poisot, T., Stouffer, D.B. \& Gravel, D. (2015). Beyond species: Why
+ecological interaction networks vary through space and time.
+\emph{Oikos}, 124, 243--251.
+
 \end{CSLReferences}

### 2022-05-06 preprint.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@32d815466d82b076cbea6971b274867eee4da2a9 🚀

@@
 
-\noindent {\LARGE \textbf{\textsf{Forecasting the spatio-temporal
-uncoupling of bumblebee-flower interaction networks}}}
+\noindent {\LARGE \textbf{\textsf{Building a better metaweb: predicting
+spatially and temporally explicit alpine plant-pollinator interaction
+networks}}}
 
@@
 %
-\,\textsuperscript{5,6,2}, %
+\,\textsuperscript{3}, %
 \href{https://orcid.org/0000-0002-2151-6693}{Dominique\,Caron}%
@@
 \,\textsuperscript{5,2}, %
-\href{https://orcid.org/0000-0001-6075-8081}{Andrew\,Gonzalez}%
-%
-\,\textsuperscript{1,2}, %
 \href{https://orcid.org/0000-0002-4498-7076}{Dominique\,Gravel}%
@@
 \,\textsuperscript{1,2}, %
-\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
+\href{https://orcid.org/0000-0001-6067-1349}{Tanya\,Strydom}%
 %
 \,\textsuperscript{5,2}, %
-\href{https://orcid.org/0000-0001-6067-1349}{Tanya\,Strydom}%
+\href{https://orcid.org/0000-0002-0735-5184}{Timothée\,Poisot}%
 %
@@
 %
-\,\textsuperscript{7}
+\,\textsuperscript{7}, %
+\href{https://orcid.org/0000-0001-6075-8081}{Andrew\,Gonzalez}%
+%
+\,\textsuperscript{1,2}
 \vskip 1em

### 2022-05-06 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@a6ff52cba4a8aff6ea61aa5a49940c782705e61e 🚀
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@b13788b40ddec32d74b5c7534b57b6aecf35d419 🚀

@@
 {\Large\bfseries\sffamily Building a better metaweb: predicting
-spatially and temporally explicit alpine plant-pollinator interaction
-networks}
+spatiotemporally explicit plant-pollinator networks}
 \vskip 5em
@@
 interactions is costly. Interactions vary in space and time (Poisot
-\emph{et al.} 2015)---particularlly relevent in this system {[}Paul
-phenology cite{]}. This is why there is interest in using models to
+\emph{et al.} 2015)---particularlly relevent in this system (CaraDonna
+\emph{et al.} 2014). This is why there is interest in using models to
 predict interactions from sparse data (\textbf{Strydom2021?}). In this
@@
 
-\textbf{\emph{Concept Fig}}
+\begin{figure}
+\centering
+\includegraphics{./figures/concept.png}
+\caption{todo}
+\end{figure}
 
@@
 
+\leavevmode\hypertarget{ref-CaraDonna2014ShiFlo}{}%
+CaraDonna, P.J., Iler, A.M. \& Inouye, D.W. (2014). Shifts in flowering
+phenology reshape a subalpine plant community. \emph{Proceedings of the
+National Academy of Sciences}, 111, 4916--4921.
+
 \leavevmode\hypertarget{ref-Gravel2019BriElt}{}%

### 2022-05-06 preprint.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@a6ff52cba4a8aff6ea61aa5a49940c782705e61e 🚀
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@b13788b40ddec32d74b5c7534b57b6aecf35d419 🚀

@@
 \noindent {\LARGE \textbf{\textsf{Building a better metaweb: predicting
-spatially and temporally explicit alpine plant-pollinator interaction
-networks}}}
+spatiotemporally explicit plant-pollinator networks}}}
 

### 2022-05-06 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@e57ea9d4eb0871f6f3c329ab1b3c3e9c36e06456 🚀

@@
 
-\hypertarget{phylogeny-construction}{%
-\subsection{Phylogeny Construction}\label{phylogeny-construction}}
-
 \hypertarget{feature-embedding}{%
@@
 
+\hypertarget{phylogeny-construction}{%
+\paragraph{Phylogeny Construction}\label{phylogeny-construction}}
+
+We construct phylogenies for both \emph{Bombus} and wildflower species
+using barcode markers, mitochondrial COI and chloroplast rbcL,
+respectively. These sequences were obtained from NCBI GenBank for all
+species. For species for which no sequence was available (only a handful
+of plants), their was substituted with a barcode from a member of the
+same genus. Justify why this is fine here.
+
+These sequences were aligned using ClustalOmega v???, and then a
+posterior distribution of phylogenies and consensus tree was obtained
+via MrBayes v??, using XX substition model with gamma-distributed rates.
+Run until convergence, which here we define as the standard-deviation of
+splits falling below 0.1.
+
+\hypertarget{creating-an-embedding-from-phylogenies}{%
+\paragraph{Creating an embedding from
+phylogenies}\label{creating-an-embedding-from-phylogenies}}
+
+We simulate traits.
+
 \hypertarget{environmental-niche-features}{%
@@
 
+We take the 19 BioClim layers from CHELSA (cite; 1km resolution) and a
+map of elevation and PCA them. A resulting 4 layers cover 99.5\% of the
+variance. We use species occurrence data from GBIF, and consider each
+occurrence record as a point in environment space. Then we fit a
+multivariate normal distribution to these points in environmental space.
+
 \hypertarget{temporal-niche-features}{%
 \subsubsection{Temporal niche features}\label{temporal-niche-features}}
+
+We take the mean and variance of the distribution of number of
+observations per week of year in the interaction field data.
 
@@
 
+We fit a bunch of models using MLJ.jl.
+
+Some of them are bagged, some are not bagged.
+
+AUC-ROC and AUC-PR values below in fig.~\ref{fig:prroc}
+
 \begin{figure}
+\hypertarget{fig:prroc}{%
 \centering
 \includegraphics{./figures/PR_ROC.png}
-\caption{todo}
+\caption{todo}\label{fig:prroc}
+}
 \end{figure}

### 2022-05-06 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@bc9240fb23f3a10cd351dcf87d589d8085c768cf 🚀

@@
 
+What does this tell us? The ensemble model is regularlly the best for
+ROC, but not for PR. This illustrates a tradeoff between models being as
+``right'' as possible versus a model being useful for discovering
+false-negatives.
+
 \hypertarget{spatiotemporally-explicit-networks}{%
@@
 
-Now that we have a metaweb\ldots..
+Now that we have a metaweb, we can extend this to predict interactions
+at partilar places and times by decomposing the probability of
+interaction at particular place and time into probability of interaction
+times probability of cooccurrence via properties of conditional prob.
+(Gravel \emph{et al.} 2019)
+
+\(P(A_{ij})P(O_{ij})\) vs \(P(A_{ij})P(O_i)P(O_j)\)
 

### 2022-05-06 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@c335897429349e7d445b169fb0705b221bb98c04 🚀

--- 2022-05-06 draft.tex
@@
 
-\hypertarget{relative-abundance}{%
-\subsubsection{Relative Abundance}\label{relative-abundance}}
+\hypertarget{environmental-niche-features}{%
+\subsubsection{Environmental niche
+features}\label{environmental-niche-features}}
+
+We take the 19 BioClim layers from CHELSA (cite; 1km resolution) and a
+map of elevation and PCA them. A resulting 4 layers cover 99.5\% of the
+variance. We use species occurrence data from GBIF, and consider each
+occurrence record as a point in environment space. Then we fit a
+multivariate normal distribution to these points in environmental space.
+
+\hypertarget{temporal-niche-features}{%
+\subsubsection{Temporal niche features}\label{temporal-niche-features}}
+
+We take the mean and variance of the distribution of number of
+observations per week of year in the interaction field data.
 
@@
 
-We simulate traits.
+We simulate traits. Relationship between number of traits, num output
+PCA dimensions, and number of used dimensions in the model matter.
+Describe how that works.
 
-\hypertarget{environmental-niche-features}{%
-\subsubsection{Environmental niche
-features}\label{environmental-niche-features}}
+\hypertarget{relative-abundance}{%
+\subsubsection{Relative Abundance}\label{relative-abundance}}
 
-We take the 19 BioClim layers from CHELSA (cite; 1km resolution) and a
-map of elevation and PCA them. A resulting 4 layers cover 99.5\% of the
-variance. We use species occurrence data from GBIF, and consider each
-occurrence record as a point in environment space. Then we fit a
-multivariate normal distribution to these points in environmental space.
-
-\hypertarget{temporal-niche-features}{%
-\subsubsection{Temporal niche features}\label{temporal-niche-features}}
-
-We take the mean and variance of the distribution of number of
-observations per week of year in the interaction field data.
+This embedding is the simplest.
 
@@
 
+What does this tell us? The ensemble model is regularly the best for
+ROC, but not for PR. This illustrates an inherent trade-off between
+models being as ``right'' as possible versus a model being useful for
+discovering false-negatives.
+
 \hypertarget{spatiotemporally-explicit-networks}{%
@@
 
-Now that we have a metaweb\ldots..
+Now that we have a metaweb, we can extend this to predict interactions
+at particular places and times by decomposing the probability of
+interaction at particular place and time into probability of interaction
+multiplied by probability of co-occurrence via properties of conditional
+probability (Gravel \emph{et al.} 2019).
+
+How do we define? \(P(i \leftrightarrow j)\) Is it
+\(P(A_{ij})P(O_{ij})\) or \(P(A_{ij})P(O_i)P(O_j)\)
 
@@
 \section{Sampling Prioiritization}\label{sampling-prioiritization}}
+
+How do we improve out udnerstanding of this pollination network, or
+determine if it is changing over time?
 

### 2022-05-06 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@1ab5ab8b4e8faed361f60000cf175df3738839b2 🚀

@@
 
-\hypertarget{metaweb-model}{%
-\section{Metaweb Model}\label{metaweb-model}}
+\hypertarget{predicting-the-metaweb}{%
+\section{Predicting the metaweb}\label{predicting-the-metaweb}}
 
@@
 
-\hypertarget{spatiotemporally-explicit-networks}{%
-\section{Spatiotemporally Explicit
-Networks}\label{spatiotemporally-explicit-networks}}
+\hypertarget{predicting-networks-in-space-and-time}{%
+\section{Predicting networks in space and
+time}\label{predicting-networks-in-space-and-time}}
 
@@
 
-\hypertarget{sampling-prioiritization}{%
-\section{Sampling Prioiritization}\label{sampling-prioiritization}}
+\hypertarget{prioritizing-spatial-sampling-of-pollinator-interactions}{%
+\section{Prioritizing spatial sampling of pollinator
+interactions}\label{prioritizing-spatial-sampling-of-pollinator-interactions}}
 
-How do we improve out udnerstanding of this pollination network, or
+How do we improve out understanding of this pollination network, or
 determine if it is changing over time?
@@
 \hypertarget{discussion}{%
-\section*{Discussion}\label{discussion}}
-\addcontentsline{toc}{section}{Discussion}
+\section{Discussion}\label{discussion}}
+
+We predict things alright. Emphasizes how heterogenous data sources can
+improve interaction prediction (rocpr fig). Advances network embedding
+as a framework for prediction of species interaction networks.
 

### 2022-06-25 figures/figuremakers/stackedsdms.jl
some ssdms

@@ -1,0 +1,60 @@
+using GeoJSON
+using Downloads
+using SimpleSDMLayers
+using Shapefile
+using Plots
+
+counties = Downloads.download("https://raw.githubusercontent.com/earthlab/earthpy/main/earthpy/example-data/colorado-counties.geojson")
+geo = GeoJSON.read(read(counties, String))
+
+p0 = colorant"#e8e8e8"
+bv_pal_1 = (p0=p0, p1=colorant"#64acbe", p2=colorant"#c85a5a")
+bv_pal_2 = (p0=p0, p1=colorant"#73ae80", p2=colorant"#6c83b5")
+bv_pal_3 = (p0=p0, p1=colorant"#9972af", p2=colorant"#c8b35a")
+bv_pal_4 = (p0=p0, p1=colorant"#be64ac", p2=colorant"#5ac8c8")
+
+beerichness = geotiff(SimpleSDMPredictor, joinpath("..", "data", "beerichness.tif"))
+beeuncert = geotiff(SimpleSDMPredictor, joinpath("..", "data", "beeuncertainty.tif"))
+plantrichness = geotiff(SimpleSDMPredictor, joinpath("..", "data", "plantrichness.tif"))
+plantuncert = geotiff(SimpleSDMPredictor, joinpath("..", "data", "plantuncertainty.tif"))
+
+
+beemax = max(beerichness.grid...)
+
+co_shp = Shapefile.shapes(Shapefile.Table(joinpath("co/co.shp")))
+
+beeplt = plot(beerichness; title="Bombus", leg=false, fc=:darkgrey, frame=:grid, xlab="Longitude", ylab="Latitude", xlim=(-109, -102), grid=false)
+bivariate!(beerichness, beeuncert, classes=4, quantiles=false; bv_pal_1...)
+p2 = bivariatelegend!(
+    beerichness, beeuncert;
+    bv_pal_1...,
+    classes=4,
+    inset=(1, bbox(0.0, 0.0, 0.27, 0.27, :center, :right)),
+    subplot=2,
+    xlab="Richness",
+    ylab="Uncertainty",
+    guidefontsize=10,
+)
+
+beeplt
+
+plantplt = plot(plantrichness; title="Flowers", leg=false, c=:darkgrey, frame=:grid, xlab="Longitude", ylab="Latitude", grid=false)
+plot!()
[…]

### 2022-06-25 tmp.jl

@@ -1,0 +1,11 @@
+using NeutralLandscapes
+using Plots
+
+sz = 80, 140
+mpd(x) = rand(MidpointDisplacement(x), sz)
+
+heatmap(mpd(0.6), c=:thermal, cbar=:none, aspectratio=1, frame=:none, axis=:none)
+
+savefig("t+1.png")
+
+pwd

### 2022-06-25 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@4133488794dda87aa98a04045a49e026179857d2 🚀
Deploying to gh-pages from @ gottacatchenall/ms_bumblebees@fac76101eed06dd1ebdabb25591c7cfc5bb771a6 🚀

@@
 
-Species interactions are important. It is ultimately interactions
-between individuals of different species that drive the structure,
-dynamics, and persistence of ecosystems, and the abundance and diversity
-of the species within them. Plant-pollinator interactions specifically
-drive the function and persistence of ``architecture of biodiversity''
-(Bascompte \& Jordano 2007). However, we are far from a robust
-understanding of plant-pollinator networks. This is because sampling
-interactions is costly. Interactions vary in space and time (Poisot
-\emph{et al.} 2015)---particularlly relevent in this system (CaraDonna
-\emph{et al.} 2014). This is why there is interest in using models to
-predict interactions from sparse data (\textbf{Strydom2021?}). In this
-paper, we combine several datasets, each spanning several years, to
-produce spatially and temporally explicit predictions of the bumblebee
-(genus \emph{Bombus}) and wildflower pollination network across the
-state of Colorado.
+Ecosystems emerge from sets of interactions between pairs of species.
+these interactions produce the dynamics and persistence of ecosystems,
+and the abundance and diversity of the species within them.
+Plant-pollinator interactions specifically drive the function and
+persistence of ``architecture of biodiversity'' (Bascompte \& Jordano
+2007). However, we are far from a robust understanding of
+plant-pollinator networks. This is because sampling interactions is
+costly. Interactions vary in space and time (Poisot \emph{et al.}
+2015)---particularly relevant in this system (CaraDonna \emph{et al.}
+2014). This is why there is interest in using models to predict
+interactions from sparse data (\textbf{Strydom2021?}). In this paper, we
+combine several datasets, each spanning several years, to produce
+spatially and temporally explicit predictions of the bumblebee (genus
+\emph{Bombus}) and wildflower pollination network across the state of
+Colorado.
 
@@
 
-\hypertarget{data}{%
-\section{Data}\label{data}}
+\hypertarget{data-and-methodology}{%
+\section{Data and methodology}\label{data-and-methodology}}
 
@@
 \emph{Bombus} metaweb.
-
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
 
@@
 
-We fit a bunch of models using MLJ.jl.
+We fit a bunch of models using MLJ.jl. Some of them are bagged, some are
+not bagged.
 
-Some of them are bagged, some are not bagged.
+We train each model on each possible combination of features.
 
@@
 
+\textbf{\emph{Figure 3: Embedded networks pre and post prediction a la
+that virus paper}}
+
 \hypertarget{predicting-networks-in-space-and-time}{%
@@
 
+\hypertarget{spatial-prediction}{%
+\subsection{Spatial prediction}\label{spatial-prediction}}
+
+Boosted regression tree using EvoTrees.jl, using data from GBIF.
+
 How do we define? \(P(i \leftrightarrow j)\) Is it
@@
 
-\textbf{\emph{Figure 3: Maps over time figure and Prob(Connectance)
+\hypertarget{temporal-prediction}{%
+\subsection{Temporal prediction}\label{temporal-prediction}}
+
+\begin{figure}
+\centering
+\includegraphics{./figures/ssdms.png}
+\caption{todo}
+\end{figure}
+
+\textbf{\emph{Figure 5: Maps over time figure and Prob(Connectance)
 vs.~Month figure}}
@@
 as a framework for prediction of species interaction networks.
+
+Embedding is a good tool for x. How do we select the dimensionality of
+our predictors? {[}Paper on ecological dimensionality{]}. But this
+doesn't mean 7-dimensions is adaquete to describe our predictors in
+models to predict species interactions.
 
